%\documentclass[A4,10pt,conference]{IEEEtran}

\documentclass[A4,11pt]{article}
\textwidth=6in
\textheight=9in
\topmargin=0in
\oddsidemargin=0in

%\usepackage[dvips]{graphicx}

\usepackage[dvips]{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{amssymb}
\usepackage{url}
\usepackage{capt-of}            %% use this to put caption outside float
\usepackage{placeins}           %% supress !!TOO MANY UNCOMPRESSED ERRORS!!
\usepackage{supertabular}       %% Insert Long Table
\usepackage{rotating}           %% To turn the tables or figures sideways
\usepackage{booktabs}
\usepackage{enumerate}
\usepackage{subfig}             %% to be used, if \subfloat has to be used to out two fugures side-by-side.
\usepackage{lscape}             %% to change the orientation of the page (potrait---->landscape)
\usepackage{lipsum}
\usepackage{mathtools}
\usepackage{vector}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%

\newcommand{\clearemptydoublepage}{\newpage{\cleardoublepage}}

%\renewcommand{\baselinestretch}{1.85}

\newtheorem{theorem}{Theorem}[section]

\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{procedure}{Procedure}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{algorithm}{Algorithm}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{property}{Property}


% set the paper title here
\title{A Literature Survey of Benchmark Functions For Global Optimization Problems}


% Paper title.

\author
{Momin Jamil$^{*\dag}$, Xin-She Yang$^{\ddag}$ 
    %Author 1, Author 2, Author 3\\
    $^{*}$Blekinge Institute of Technology\\
    SE-37179, Karlskrona, Sweden\\
    %E-mail: hans-jurgen.zepernick@bth.se\\
    %
    $^{\dag}$Harman International, Cooperate Division\\
    Becker-Goering Str. 16, D-76307 Karlsbad, Germany\\
    E-mail: momin.jamil@harman.com\\
    %
    $^{\ddag}$Middlesex University\\
    School of Science and Technology\\
    Hendon Campus, London NW4 4BT, UK\\
    E-mail: xin-she.yang@middlesex.ac.uk %% ASK FOR NEW EMAIL ADDRESS
}

\date{{\bf Citation details:} \\ 
Momin Jamil and Xin-She Yang,
A literature survey of benchmark functions for global optimization problems,
{\it Int. Journal of Mathematical Modelling and Numerical Optimisation},
Vol.~4, No.~2, pp. 150--194 (2013). \\ 
DOI: 10.1504/IJMMNO.2013.055204 
}

\begin{document}

\maketitle
Test functions are important to validate and compare the performance of  optimization algorithms.
There have been many test or benchmark functions reported in the literature; however,
there is no standard list or set of benchmark functions. Ideally, test functions should have
diverse properties so that can be truly useful to test new algorithms in an unbiased way.
For this purpose, we have reviewed and compiled a rich set of 175 benchmark functions
for unconstrained optimization problems with diverse properties in terms of modality,
separability, and valley landscape. This is by far the most complete set of functions
so far in the literature, and tt can be expected this complete set of functions can
be used for validation of new optimization in the future.

\input{part1_v2}             %   Introduction
\input{part2_v2}             %   Benchmark Functions
\input{part3_ref_v2}           %   References

\end{document}
