\begin{thebibliography}{99}

%@ARTICLE{Ortiz-boyer05cixl2-,
%    author = {Domingo Ortiz-boyer and César Hervás-martínez and Nicolás García-pedrajas},
%    title = {CIXL2 - A crossover operator for evolutionary algorithms based on population features},
%    journal = {Journal of Artifical Intelligence Research},
%    year = {2005},
%    volume = {24},
%    pages = {1-48}
%}


\bibitem{ACKLEY1987} D. H. Ackley, ``A Connectionist Machine for Genetic Hill-Climbing,'' Kluwer, 1987.

\bibitem{ADJIMAN1998} C. S. Adjiman, S. Sallwig, C. A. Flouda, A. Neumaier, ``A Global Optimization Method, aBB for General Twice-Differentiable NLPs-1, Theoretical Advances,''
Computers Chemical Engineering, vol. 22, no. 9, pp. 1137-1158, 1998.

\bibitem{ADORIO2005} E. P. Adorio, U. P. Dilman, ``MVF - Multivariate Test Function Library in C for Unconstrained Global Optimization Methods,''
[Available Online]: \url{http://www.geocities.ws/eadorio/mvf.pdf}

\bibitem{ALI2005} M. M. Ali, C. Khompatraporn, Z. B. Zabinsky,
``A Numerical Evaluation of Several Stochastic Algorithms on Selected Continuous Global Optimization Test Problems,''
Journal of Global Optimization, vol. 31, pp. 635-672, 2005.

\bibitem{ANDREI2008} N. Andrei, ``An Unconstrained Optimization Test Functions Collection,''
Advanced Modeling and Optimization, vol. 10, no. 1, pp.147-161, 2008.

\bibitem{AUGER2007} A. Auger, N. Hansen, N. Mauny, R. Ros, M. Schoenauer, ``Bio-Inspired Continuous Optimization: The Coming of Age,''
Invited Lecture, IEEE Congress on Evolutionary Computation, NJ, USA, 2007.

\bibitem{AVERICK1991} B. M. Averick, R. G. Carter, J. J. Mor\'{e}, ``The MINIPACK-2 Test Problem Collection,''
Mathematics and Computer Science Division, Agronne National Laboratory, Technical Memorandum No. 150, 1991.

\bibitem{AVERICK1992} B. M. Averick, R. G. Carter, J. J. Mor\'{e}, G. L. Xue, ``The MINIPACK-2 Test Problem Collection,''
Mathematics and Computer Science Division, Agronne National Laboratory, Preprint MCS-P153-0692, 1992.

\bibitem{BAECK1993} T. B\"{a}ck, H. P. Schwefel, ``An Overview of Evolutionary Algorithm for Parameter Optimization,''
Evolutionary Computation, vol. 1, no. 1, pp. 1-23, 1993.

\bibitem{BEGAMBRE2009} O. Begambre, J. E. Laier, ``A hybrid Particle Swarm Optimization - Simplex Algorithm (PSOS) for Structural Damage
    Identification,''
Journal of Advances in Engineering Software, vol. 40, no. 9, pp. 883-891, 2009.

\bibitem{BEKEY1974} G. A. Bekey, M. T. Ung, ``A Comparative Evaluation of Two Global Search Algorithms,''
IEEE Transaction on Systems, Man and Cybernetics, vol. 4, no. 1, pp. 112-116, 1974.

\bibitem{BERSINI1996} H. Bersini, M. Dorigo, S. Langerman, ``Results of the First International Contest on Evolutionary Optimization,''
IEEE International Conf. on Evolutionary Computation, Nagoya, Japan, pp. 611-615, 1996.

\bibitem{BIGGS1971} M. C. Biggs, ``A New Variable Metric Technique Taking Account of Non-Quadratic Behaviour of the Objective function,''
IMA Journal of Applied Mathematics, vol. 8, no. 3, pp. 315-327, 1971.

\bibitem{BOHACHEVSKY1986} I. O. Bohachevsky, M. E. Johnson, M. L. Stein, ``General Simulated Annealing for Function Optimization,''
Technometrics, vol. 28, no. 3, pp. 209-217, 1986.

\bibitem{BRANIN1972} F. H. Branin Jr., ``Widely Convergent Method of Finding Multiple Solutions of Simultaneous Nonlinear Equations,''
IBM Journal of Research and Development, vol. 16, no. 5, pp. 504-522, 1972.

\bibitem{BOYER2005}  D. O. Boyer, C. H. Martfnez, N. G. Pedrajas, ''Crossover Operator for Evolutionary Algorithms Based on Population Features'',
Journal of Artificial Intelligence Research, vol. 24, pp. 1-48, 2005.

\bibitem{BRAD1970} Y. Brad, ``Comparison of Gradient Methods for the Solution of Nonlinear Parametric Estimation Problem,''
SIAM Journal on Numerical Analysis, vol. 7, no. 1, pp. 157-186, 1970.

\bibitem{CET2004} The Cross-Entropy Toolbox\url{http://www.maths.uq.edu.au/CEToolBox/}

\bibitem{CHEN2003} Y. Chen ``Computer Simulation of Electron Positron Annihilation Processes,''
Technical Report SLAC-Report-646, Stanford Linear Accelerator Center, Stanford University, 2003.
[Available Online]: \url{http://www.slac.stanford.edu/pubs/slacreports/slac-r-646.html}

\bibitem{CHUNG1998} C. J. Chung, R. G. Reynolds, ``CAEP: An Evolution-Based Tool for Real-Valued Function Optimization Using Cultural Algorithms,''
    International Journal on Artificial Intelligence Tool, vol. 7, no. 3, pp. 239-291, 1998.

\bibitem{CLERC1999} M. Clerc, ``The Swarm and the Queen, Towards a Deterministic and Adaptive Particle Swarm Optimization, ''
IEEE Congress on Evolutionary Computation, Washington DC, USA, pp. 1951-1957, 1999.

\bibitem{CORANA1987} A. Corana, M. Marchesi, C. Martini, S. Ridella, ``Minimizing Multimodal Functions of Continuous Variables with Simulated Annealing Algorithms,''
    ACM Transactions on Mathematical Software, vol. 13, no. 3, pp. 262-280, 1987.

\bibitem{COURRIEU1997} P. courrieu, ``The Hyperbell Algorithm for Global Optimization: A Random Walk Using Cauchy Densities,''
Journal of Global Optimization, vol. 10, no. 1, pp. 111-133, 1997.


\bibitem{CRAGG1969} E. E. Cragg, A. V. Levy, ``Study on Supermemory Gradient Method for the Minimization of Functions,''
Journal of Optimization Theory and Applications, vol. 4, no. 3, pp. 191-205, 1969.

\bibitem{CSENDES1997} T. Csendes, D. Ratz, ``Subdivision Direction Selection in Interval Methods for Global Optimization,''
SIAM Journal on Numerical Analysis, vol. 34, no. 3, pp. 922-938.

\bibitem{DAMAVANDI2005}  N. Damavandi, S. Safavi-Naeini, ``A Hybrid Evolutionary Programming Method for Circuit Optimization,''
IEEE Transaction on Circuit and Systems I, vol. 52, no. 5, pp. 902-910, 2005.

\bibitem{deVILLERS1981} N. deVillers, D. Glasser, ``A Continuation Method for Nonlinear Regression,''
SIAM Journal on Numerical Analysis, vol. 18, no. 6, pp. 1139-1154, 1981.

\bibitem{DIXON1989} L. C. W. Dixon, R. C. Price, ``The Truncated Newton Method for Sparse Unconstrained Optimisation Using Automatic Differentiation,''
Journal of Optimization Theory and Applications, vol. 60, no. 2, pp. 261-275, 1989.

\bibitem{DIXON1978} L. C. W. Dixon, G. P. Szeg\"{o} (eds.), ``Towards Global Optimization 2,''
Elsevier, 1978.

\bibitem{EL-ATTAR1979} R. A. El-Attar, M. Vidyasagar, S. R. K. Dutta, ``An Algorithm for II-norm Minimization With Application to Nonlinear II-approximation,''
SIAM Journal on Numverical Analysis, vol. 16, no. 1, pp. 70-86, 1979.

\bibitem{ELWAKEIL1996} ``Two Algorithms for Global Optimization of General NLP Problems,''
International Journal on Numerical Methods in Engineering, vol. 39, no. 19, pp. 3305-3325, 1996.

\bibitem{FLETCHER1963} R. Fletcher, M. J. D. Powell, ``A Rapidly Convergent Descent Method for Minimzation,''
Computer Journal, vol. 62, no. 2, pp. 163-168, 1963.
[Available Online]: \url{http://galton.uchicago.edu/~lekheng/courses/302/classics/fletcher-powell.pdf}

\bibitem{FLOUDAS1999} C. A. Flouda, P. M. Pardalos, C. S. Adjiman, W. R. Esposito, Z. H. G\"{u}m\"{u}s, S. T. Harding, J. L. Klepeis, C. A. Meyer, and C. A. Schweiger,
``Handbook of Test Problems in Local and Global Optimization,'' Kluwer, Boston, 1999.

\bibitem{FRALEY1989} C. Fraley, ``Software Performances on Nonlinear Least-Squares Problems,''
Technical Report no. STAN-CS-89-1244, Department of Computer Science, Stanford University, 1989.
[Available Online]: \url{http://www.dtic.mil/dtic/tr/fulltext/u2/a204526.pdf}

\bibitem{FU2006} M. C. Fu, J. Hu, S. I. Marcus, ``Model-Based Randomized Methods for Global Optimization,''
Proc. 17th International Symp. Mathematical Theory Networks Systems, Kyoto, Japan, pp. 355-365, 2006.

\bibitem{GAMS2000} GAMS World, GLOBAL Library,
[Available Online]: \url{http://www.gamsworld.org/global/globallib.html.}

\bibitem{GEATbx} GEATbx - The Genetic and Evolutionary Algorithm Toolbox for Matlab,
[Available Online]: \url{http://www.geatbx.com/}


\bibitem{GOLDSTEIN1971} A. A. Goldstein, J. F. Price, ``On Descent from Local Minima,''
Mathematics and Comptutaion, vol. 25, no. 115, pp. 569-574, 1971.

\bibitem{GORDON1993} V. S. Gordon, D. Whitley, ´´Serial and Parallel Genetic Algoritms as Function Optimizers,''
In S. Forrest (Eds), 5th Intl. Conf. on Genetic Algorithms, pp. 177-183, Morgan Kaufmann.

\bibitem{GRIEWANK1981} A. O. Griewank, ``Generalized Descent for Global Optimization,''
Journal of Optimization Theory and Applications, vol. 34, no. 1, pp. 11-39, 1981.


\bibitem{GOULD2001} N. I. M. Gould, D. Orban, and P. L. Toint, ``CUTEr, A Constrained and Un-constrained Testing Environment, Revisited,''
[Available Online]: \url{http://cuter.rl.ac.uk/cuter-www/problems.html.}


\bibitem{HARTMAN1972} J. K. Hartman, ``Some Experiments in Global Optimization,''
[Available Online]: \url{http://ia701505.us.archive.org/9/items/someexperimentsi00hart/someexperimentsi00hart.pdf}

\bibitem{HEDAR} A.-R. Hedar, ``Global Optimization Test Problems,''
[Available Online]: \url{http://www-optima.amp.i.kyoto-u.ac.jp/member/student/hedar/Hedar_files/TestGO.htm.}

\bibitem{HENNART1982} J. P. Hennart (ed.), ``Numerical Analysis,''
Proc. 3rd AS Workshop, Lecture Notes in Mathematics, vol. 90, Springer, 1982.

\bibitem{HIMMELBLAU1972} D. M. Himmelblau, ``Applied Nonlinear Programming,''
McGraw-Hill, 1972.

\bibitem{JENNRICH1968} R. I. Jennrich, P. F. Sampson, ``Application of Stepwise Regression to Non-Linear estimation,''
Techometrics, vol. 10, no. 1, pp. 63-72, 1968.
\url{http://www.jstor.org/discover/10.2307/1266224?uid=3737864&uid=2129&uid=2&uid=70&uid=4&sid=21101664491701}

\bibitem{JUNIOR2004} A. D. Junior, R. S. Silva, K. C. Mundim, and  L. E. Dardenne, ``Performance and Parameterization of the Algorithm Simplified Generalized Simulated Annealing,''
Genet. Mol. Biol., vol. 27, no. 4, pp. 616--622, 2004.
[Available Online]:  \url{http://www.scielo.br/scielo.php?script=sci_arttext&pid=S1415-47572004000400024&lng=en&nrm=iso.}
ISSN 1415-4757.  \url{http://dx.doi.org/10.1590/S1415-47572004000400024.}

\bibitem{KAJ} Test Problems for Global Optimization,
\url{http://www2.imm.dtu.dk/~kajm/Test_ex_forms/test_ex.html}



\bibitem{LAVI1966} A. Lavi, T. P. Vogel (eds), ``Recent Advances in Optimization Techniques,''
John Wliley \& Sons, 1966.

\bibitem{LOOTSMA1972} F. A. Lootsma (ed.), `` Numerical Methods for Non-Linear Optimization,''
Academic Press, 1972.

\bibitem{MOORE1988} R. E. Moore, ``Reliability in Computing,''
Academic Press, 1998.

\bibitem{MORE1981} J. J. Mor{\'e}, B. S. Garbow, K. E. Hillstrom, ``Testing Unconstrained Optimization Software,'',
ACM Trans. on Mathematical Software, vol. 7, pp. 17-41, 1981.
%ACM Trans. on Mathematical Software, vol. 7, no. 1, pp. 17-41, Mar. 1981.

\bibitem{MISHRA2006_1} S. K. Mishra, ``Performance of Differential Evolution and Particle Swarm Methods on Some Relatively Harder Multi-modal Benchmark Functions,''
[Available Online]: \url{http://mpra.ub.uni-muenchen.de/449/}

\bibitem{MISHRA2006_2} S. K. Mishra, ``Performance of the Barter, the Differential Evolution and the Simulated Annealing Methods of
Global Pptimization On Some New and Some Old Test Functions,''
[Available Online]: \url{http://www.ssrn.com/abstract=941630}

\bibitem{MISHRA2006_3} S. K. Mishra, ``Repulsive Particle Swarm Method On Some Difficult Test Problems of Global Optimization,''
[Available Online]: \url{http://mpra.ub.uni-muenchen.de/1742/}

\bibitem{MISHRA2006_4} S. K. Mishra, ``Performance of Repulsive Particle Swarm Method in Global Optimization of Some Important Test Functions:
A Fortran Program,''
[Available Online]: \url{http://www. ssrn.com/abstract=924339}

\bibitem{MISHRA2006_5} S. K. Mishra, ``Global Optimization by Particle Swarm Method: A Fortran Program,''  Munich Research Papers in Economics,
[Available Online]: \url{http://mpra.ub.uni-muenchen.de/874/}

\bibitem{MISHRA2006_6} S. K. Mishra, ``Global Optimization By Differential Evolution and Particle Swarm Methods:
Evaluation On Some Benchmark Functions,'' Munich Research Papers in Economics,
[Available Online]: \url{http://mpra.ub.uni-muenchen.de/1005/}

\bibitem{MISHRA2006_7} S. K. Mishra, ``Some New Test Functions For Global Optimization And Performance of Repulsive Particle Swarm Method,''
[Available Online]: \url{http://mpra.ub.uni-muenchen.de/2718/}

\bibitem{MUNTEANU1998} C. Muntenau, V. Lazarescu, ``Global Search Using a New Evolutionayr Framework: The Adaptive Reservoir Genetic Algorithm,''
Complexity International, vol. 5, 1998.
[Available Online]: \url{http://www.complexity.org.au/ci/vol05/munteanu/munteanu.html}

\bibitem{NEUMAIER2003_1} A. Neumaier, ``COCONUT Benchmark,''
[Available Online]: \url{http://www.mat.univie.ac.at/~neum/glopt/coconut/benchmark.html.}

\bibitem{OPACIC1973} J. Opa\v{c}i\'{c}, ``A Heuristic Method for Finding Most extrema of a Nonlinear Functional,''
IEEE Transactions on Systems, Man and Cybernetics, vol. 3, no. 1, pp. 102-107, 1973.

\bibitem{PINTER1996} J. D. Pint\'{e}r, ``Global Optimization in Action: Continuous and Lipschitz Optimization Algorithms, Implementations and Applications,''
Kluwer, 1996.

\bibitem{POWELL1962} M. J. D. Powell, ``An Iterative Method for Finding Stationary Values of a Function of Several Variables,''
Computer Journal, vol. 5, no. 2, pp. 147-151, 1962.
[Available Online]: \url{http://comjnl.oxfordjournals.org/content/5/2/147.full.pdf}

\bibitem{POWELL1964} M. J. D. Powell, ``An Efficient Method for Finding the Minimum of a Function for Several Variables Without Calculating Derivatives,''
Computer Journal, vol. 7, no. 2, pp. 155-162, 1964.
%[Available Online]: \url{http://comjnl.oxfordjournals.org/content/5/2/147.full.pdf}

\bibitem{PRICE2005} K. V. Price, R. M. Storn, J. A. Lampinen, ``Differential Evolution: A Practical Approach to Global Optimization,''
Springer, 2005.

\bibitem{PRICE1977} W. L. Price, ``A Controlled Random Search Procedure for Global Optimisation,''
Computer journal, vol. 20, no. 4, pp. 367-370, 1977.
[Available Online]: \url{http://comjnl.oxfordjournals.org/content/20/4/367.full.pdf}

\bibitem{QING2006} A. Qing, ``Dynamic Differential Evolution Strategy and Applications in Electromagnetic Inverse Scattering Problems,''
IEEE Transactions on Geoscience and remote Sensing, vol. 44, no. 1, pp. 116-125, 2006.

\bibitem{RAHNAMAYAN2007} S. Rahnamyan, H. R. Tizhoosh, N. M. M. Salama, ``A Novel Population Initialization Method for Accelerating Evolutionary Algorithms,''
Computers and Mathematics with Applications, vol. 53, no. 10, pp. 1605-1614, 2007.

\bibitem{RAHNAMAYAN2007_1} S. Rahnamyan, H. R. Tizhoosh, N. M. M. Salama, ``Opposition-Based Differential Evolution (ODE) with Variable Jumping Rate,''
IEEE Sympousim Foundations Computation Intelligence, Honolulu, HI, pp. 81-88, 2007.

\bibitem{RAO2009} S. S. Rao, ``Engineering Optimization: Theory and Practice,'' John Wiley \& Sons, 2009.

\bibitem{ROENKKOENEN2009} J. R\"{o}nkk\"{o}nen, ``Continuous Multimodal Global Optimization With Differential Evolution-Based Methods,''
PhD Thesis, Lappeenranta University of Technology, 2009.

\bibitem{ROSENBROCK1960} H. H. Rosenbrock, ``An Automatic Method for Finding the Greatest or least Value of a Function,''
Computer Journal, vol. 3, no. 3, pp. 175-184, 1960.
[Available Online]: \url{http://comjnl.oxfordjournals.org/content/3/3/175.full.pdf}

\bibitem{SALOMON1996} R. Salomon, ``Re-evaluating Genetic Algorithm Performance Under Corodinate Rotation of Benchmark Functions:
A Survey of Some Theoretical and Practical Aspects of Genetic Algorithms,''
BioSystems, vol. 39, no. 3, pp. 263-278, 1996.

\bibitem{SCHUMER1968} M. A. Schumer, K. Steiglitz, ``Adaptive Step Size Random Search,''
IEEE Transactions on Automatic Control. vol. 13, no. 3, pp. 270-276, 1968.


\bibitem{SCHAFFER1989} J. D. Schaffer, R. A. Caruana, L. J. Eshelman, R. Das, ``A Study of Control Parameters Affecting Online
Performance of Genetic Algorithms for Function Optimization,''
Proc. 3rd International Conf. on Genetic Algorithms, George Mason Uni., pp. 51-60, 19889.

\bibitem{SCHWEFEL1981} H. P. Schwefel, ``Numerical Optimization for Computer Models,''
John Wiley \ Sons, 1981.

\bibitem{SCHWEFEL1995} H. P. Schwefel, ``Evolution and Optimum Seeking,''
John Wiley \ Sons, 1995.

\bibitem{SHANNO1970} D. F. Shanno, ``Conditioning of Quasi-Newton Methods for Function Minimization,''
Mathematics of Computation, vol. 24, no. 111, pp. 647-656, 1970.

\bibitem{SILAGADZE2007} Z. K. Silagadze, ``Finding Two-Dimesnional Peaks,''
Physics of Particles and Nuclei Letters, vol. 4, no. 1, pp. 73-80, 2007.

\bibitem{STORN1996} R. Storn, K. Price, ``Differntial Evolution - A Simple and Efficient Adaptive Scheme for Global Optimization over Continuous Spaces,''
Technical Report no. TR-95-012, International Computer Science Institute, Berkeley, CA, 1996.
[Available Online] : \url{http://www1.icsi.berkeley.edu/~storn/TR-95-012.pdf}

\bibitem{SUGANTHAN2005} P. N. Suganthan, N. Hansen, J. J. Liang, K. Deb, Y.-P. Chen, A. Auger, S. Tiwari,
``Problem Definitions and Evaluation Criteria for CEC 2005, Special Session on Real-Parameter Optimization,''
Nanyang Technological University (NTU), Singapore, Tech. Rep., 2005.
[Available Online]:  \url{http://www.lri.fr/~hansen/Tech-Report-May-30-05.pdf}

\bibitem{TANG2008} K. Tang, X. Yao, P. N. Suganthan,  C. MacNish, Y.-P. Chen, C.-M. Chen, Z. Yang,
``Benchmark Functions for the CEC’2008 Special Session and Competition on Large Scale Global Optimization,'',
Tech. Rep., 2008.
[Available Online]:  \url{http://nical.ustc.edu.cn/cec08ss.php}

\bibitem{TANG2010} K. Tang, X. Li, P. N. Suganthan, Z. Yang, T. Weise,
``Benchmark Functions for the CEC’2010 Special Session and Competition on Large-Scale Global Optimization,''
Tech. Rep., 2010.
[Available Online]: \url{http://sci2s.ugr.es/eamhco/cec2010_functions.pdf}


\bibitem{WAYBURN1987} T. L. Wayburn, J. D. Seader, ``Homotopy Continuation Methods for Computer-Aided Process Design,''
Computers and Chemical Engineering, vol. 11, no. 1, pp. 7-25, 1987.

\bibitem{WHITLEY1996}, D. Whitley, K. Mathias, S. Rana, J. Dzubera, ``Evaluating Evolutionary Algorithms,''
Artificial Intelligence, vol. 85, pp. 245--276, 1996.

\bibitem{WINSTON1992} P. H. Winston, ``Artificial Intelligence, $3^{rd}$ ed.''
Addison-Wesley, 1992.

\bibitem{YANG2010a} X. S. Yang, ``Test Problems in Optimization,'' Engineering Optimization: An Introduction with Metaheuristic Applications
John Wliey \& Sons, 2010.
[Available Online]: \url{http://arxiv.org/abs/1008.0549}

\bibitem{YANG2010b} X. S. Yang, ``Firefly Algorithm, Stochastic Test Functions and Design Optimisation,''
Intl. J. Bio-Inspired Computation, vol. 2, no. 2, pp. 78-84.
[Available Online]:  \url{http://arxiv.org/abs/1008.0549}

\bibitem{YAO1996} X. Yao, Y. Liu, ``Fast Evolutionary Programming,''
Proc. $5^{th}$ Conf. on Evolutionary Programming, 1996.





\end{thebibliography}
