\section{Characteristics of Test Functions} \label{s:collection}

The goal of any global optimization (GO) is to find the best possible solutions $\textbf{x}^{*}$ from a set
$\mathbb{X}$ according to a set of criteria $F = \{f_{1}, f_{2},\cdots f_{n}\}$.  These criteria are called
objective functions expressed in the form of mathematical functions.  An objective function is a mathematical function
$f:D \subset \Re^n \rightarrow \Re$ subject to additional constraints.  The set $D$ is referred to as the set of feasible points in
a search space.  In the case of optimizing a single criterion $f$, an optimum is either its maximum or minimum.
The global optimization problems are often defined as  minimization problems, however, these problems can be easily
converted to maximization problems by negating $f$.  A general global optimum problem can be defined as follows:
\begin{eqnarray}
   \underset{\textrm{\textbf{x}}}{\textrm{minimize}} f(\textbf{x})
\end{eqnarray}
The true optimal solution of an optimization problem may be a set of
$\textbf{x}^{*} \in D $ of all optimal points in $D$, rather than a single minimum or maximum value in some cases.  There could be
multiple, even an infinite number of optimal solutions, depending on the domain of the search space.  
The tasks of any good global optimization algorithm is to find globally optimal or at least sub-optimal solutions.
The objective functions could be characterized as continuous, discontinuous, linear, non-linear, convex, non-conxex,
unimodal, multimodal, separable\footnote{In this paper, partially separable functions are also considered as separable function}
and non-separable.


According to \cite{CHUNG1998}, it is important to ask the following two questions before start solving an optimization problem;
(i) What aspects of the function landscape make the optimization process difficult? (ii) What type of
\textit{a priori} knowledge is most effective for searching particular types of function landscape?
In order to answer these questions, benchmark functions can be classified in terms of features like
modality, basins, valleys, separability and dimensionality \cite{WINSTON1992}.

\subsection{Modality}
The number of ambiguous peaks in the function landscape corresponds to the modality of a function.
If algorithms encounters these peaks during a search process, there is a tendency that the algorithm may be trapped
in one of such peaks.  This will have a negative impact on the search process, as this can direct the search
away from the true optimal solutions.

\subsection{Basins}
%A basin occurs when a function has a relatively steep decline surrounding a large area.
A relatively steep decline surrounding a large area is called a basin.
Optimization algorithms can be easily attracted to such regions.
Once in these regions, the search process of an algorithm is severely hampered.
This is due to lack of information to direct the search process towards the minimum.
According to \cite{CHUNG1998}, a basin corresponds to the plateau for a maximization problem,
and a problem can have multiple plateaus.


\subsection{Valleys}
A valley occurs when a narrow area of little change is surrounded by regions of steep descent \cite{CHUNG1998}.
As with the basins, minimizers are initially attracted to this region.  The progress of a search process of an
algorithm may be slowed down considerably on the floor of the valley.

\subsection{Separability}
The separability is a measure of difficulty of different benchmark functions.
In general, separable functions are relatively easy to solve, when compared with their
inseperable counterpart, because each
variable of a function is independent of the other variables.  If all the parameters or variables
are independent, then a sequence of $n$ independent optimization processes can be performed.
As a result, each design variable or parameter can be optimized independently.  According to \cite{SALOMON1996}, the
general condition of separability to see if the function is easy to optimize or not is given as
\begin{eqnarray}
    \frac{\partial{f(\overline{x})}}{\partial{x_{i}}} = g(x_{i})h(\overline{x}) \label{eq:separability}
\end{eqnarray}
where $g({\overline{x_{i}}})$ means any function of $x_{i}$ only and $h({\overline{x}})$ any
function of any $\overline{x}$. If this condition is satisfied, the function is called partially
separable and easy to optimize, because solutions for each $x_{i}$ can be obtained independently
of all the other parameters.  This separability condition can be illustrated by the following two examples.

For example, function $(f_{105})$ is not separable, because it does not satisfy the condition (\ref{eq:separability})
\begin{eqnarray}
    \frac{\partial{f_{105}(x_1,x_2)}}{\partial{x_1}} &=& 400(x_1^2 - x_2)x_1 - 2x_1 -2 \nonumber \\
    \frac{\partial{f_{105}(x_1,x_2)}}{\partial{x_2}} &=& -200(x_1^2 - x_2) \nonumber
\end{eqnarray}

On the other hand, the sphere function ($f_{137}$) with two variables can indeed satisfy the above
condition (\ref{eq:separability}) as shown below.
\begin{eqnarray}
    \frac{\partial{f_{137}(x_1,x_2)}}{\partial{x_1}} = 2x_1 \nonumber ~~~~~~~~ \frac{\partial{f_{137}(x_1,x_2)}}{\partial{x_2}} = 2x_2
\end{eqnarray}
where $h(x)$ is regarded as $1$.

In \cite{BOYER2005}, the formal definition of separability is given as

\begin{eqnarray}
   \underset{\textrm{${x_{1}}$,...,${x_{p}}$}}{\textrm{arg minimize}} f({x_{1},...,x_{p}}) &=& \big(\underset{\textrm{${x_{1}}$}}{\textrm{arg minimize}}f(x_{1},...),..., \nonumber \\
   & & \underset{\textrm{${x_{p}}$}}{\textrm{arg minimize}}f(...,x_{p})\big)
\end{eqnarray}
\noindent
In other words, a function of $p$ variables is called separable, if it can written as a sum of $p$ functions of just one variable \cite{BOYER2005}.  On the other hand, a function is called non-separable, if its variables show inter-relation among themselves or are not independent.  If the objective function variables are independent of each other, then the objective functions can be decomposed into sub-objective functions.  Then, each of these sub-objectives involves only one decision variable, while treating all the others as constant and can be expressed as

\begin{eqnarray}
    f(x_{1},x_{2},\cdots,x_{p}) = \sum_{i=1}^{p}f_{i}(x_{i})
\end{eqnarray}
\noindent


\subsection{Dimensionality}
The difficulty of a problem generally increases with its dimensionality.
According to \cite{WINSTON1992, YAO1996}, as the number of parameters or dimension increases,
the search space also increases exponentially.
For highly nonlinear problems, this dimensionality may be a significant barrier for
almost all optimization algorithms.

\section{Benchmark Test Functions for Global Optimization} \label{s:collection}
Now, we present a collection of $175$ unconstrained optimization test problems which can be used to validate
the performance of optimization algorithms.  The dimensions, problem domain size and optimal solution are denoted by
$D$, $Lb \leq \textbf{x}_{i} \leq Ub$ and $f(\textbf{x}^{*}) = f(x_{1},...x_{n})$, respectively.  The symbols $\textrm{Lb}$ and $\textrm{Ub}$
represent lower, upper bound of the variables, respectively.  It is worth noting that in several cases, the optimal
solution vectors and their corresponding solutions are known only as numerical approximations.

\begin{enumerate}

\item \textbf{Ackley 1 Function} \cite{BAECK1993}(Continuous, Differentiable, Non-separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{1}(x) &=& -20 e^{-0.02 \sqrt{D^{-1}\sum_{i=1}^{D}x_{i}^{2}}} - e^{D^{-1}\sum_{i=1}^{D}\cos(2 \pi x_{i})} + 20 + e \nonumber
\end{eqnarray}
subject to  $-35 \leq x_{i} \leq 35$.  The global minima is located at origin $\textbf{x}^{*} = (0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$. \\

\item \textbf{Ackley 2 Function} \cite{ACKLEY1987} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
	       f_{2}(x) &=& -200 e^ {-0.02 \sqrt{x_{1}^2 + x_{2}^2}} \nonumber
\end{eqnarray}
subject to  $-32 \leq x_{i} \leq 32$.  The global minimum is located at origin $\textbf{x}^{*} = (0,0)$,
$f(\textbf{x}^{*}) = -200$. \\

\item \textbf{Ackley 3 Function} \cite{ACKLEY1987} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
	       f_{3}(x) &=& 200 e^ {-0.02 \sqrt{x_{1}^2 + x_{2}^2}} + 5 e^{\textrm{cos}(3x_{1}) + \textrm{sin}(3x_{2})}\nonumber
\end{eqnarray}
subject to  $-32 \leq x_{i} \leq 32$.  The global minimum is located at $\textbf{x}^{*} = (0,\approx -0.4)$,
$f(\textbf{x}^{*}) \approx -219.1418$. \\

%% MODIDIFIED ACKLEY FUNCTION
\item \textbf{Ackley 4 or Modified Ackley Function} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
        \begin{eqnarray}
	       f_{4}(\textbf{x}) &=& \sum_{i=1}^D\left(e^{-0.2}\sqrt{x_{i}^2 + x_{i+1}^2} + 3\left(\textrm{cos}(2x_{i}) + \textrm{sin}(2x_{i+1})\right)\right)\nonumber
        \end{eqnarray}
    subject to  $-35 \leq x_{i} \leq 35$.  It is highly multimodal function with two global minimum close to origin

    $\textbf{x} = f(\{-1.479252,-0.739807\}, \{1.479252,-0.739807\})$, $f(\textbf{x}^{*}) = -3.917275 $. \\

\item \textbf{Adjiman Function} \cite {ADJIMAN1998}(Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{5}(x) &=& \textrm{cos}(x_{1})\textrm{sin}(x_{2}) - \frac{x_{1}}{(x_{2}^2 + 1)}\nonumber
\end{eqnarray}
subject to  $ -1\leq x_{1} \leq 2$, $ -1\leq x_{2} \leq 1$.  The global minimum is located at
$\textbf{x}^{*} = (2, 0.10578)$, $f(\textbf{x}^{*}) = -2.02181$. \\

%% ALPINE 1 FUNCTION
\item \textbf{Alpine 1 Function} \cite {RAHNAMAYAN2007}(Continuous, Non-Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{6}(\textbf{x}) &=& \sum_{i=1}^D \Big\lvert{x_i \textrm{sin}(x_i) + 0.1x_{i}}\Big\rvert \nonumber
\end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at origin $\textbf{x}^{*} = (0,\cdots,0)$,
    $f(\textbf{x}^{*}) = 0$. \\

%% ALPINE 2 FUNCTION
\item \textbf{Alpine 2 Function} \cite{CLERC1999} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{7}(\textbf{x}) &=& \prod_{i=1}^D \sqrt{x_{i}} \textrm{sin}(x_{i}) \nonumber
\end{eqnarray}
    subject to  $0 \leq x_{i} \leq 10$.  The global minimum is located at  $\textbf{x}^{*} = (7.917 \cdots 7.917)$,
    $f(\textbf{x}^{*}) = 2.808^{D}$. \\

%% BRAD FUNCTION
\item \textbf{Brad Function} \cite{BRAD1970} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{8}(\textbf{x}) &=& \sum_{i=1}^{15} \left[\frac{y_{i} - x_{1} - u_{i}}{v_{i}x_{2} + w_{i}x_{3}}\right]^2 \nonumber
\end{eqnarray}
where $u_{i} = i$, $v_{i} = 16 - i$, $w_{i}$ = min($u_{i},v_{i}$) and  $\textbf{\underline{y}} = y_{i}$ = $[0.14$, $0.18$, $0.22$,
$0.25, 0.29$, $0.32, 0.35$, $0.39, 0.37$, $0.58, 0.73, 0.96$, $1.34, 2.10, 4.39]^T$.
It is subject to  $-0.25 \leq x_{1} \leq 0.25$, $0.01 \leq x_{2},x_{3} \leq 2.5$.  The global minimum is located at
$\textbf{x}^{*} = (0.0824, 1.133,2.3437)$, $f(\textbf{x}^{*}) = 0.00821487$. \\

%% Bartels Conn Function
\item \textbf{Bartels Conn Function} (Continuous, Non-differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{9}(\textbf{x}) &=& \bigl \lvert {x_{1}^2 + x_{2}^2 + x_{1}x_{2}}\bigr \rvert  + \bigl \lvert {\textrm{sin}(x_{1})}\bigr \rvert +
                                \bigl \lvert {\textrm{cos}(x_{2})}\bigr \rvert\nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is located at  $\textbf{x}^{*} = (0,0)$,
    $f(\textbf{x}^{*}) = 1$. \\

%%BEALE FUNCTION
\item \textbf{Beale Function} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    %f_{}(\textbf{x}) &=& (1.5 - x_{1} + x_{1}x_{2})^{2} + (2.25 - x_{1} + x_{1}x_{2}^2)^{2}  \nonumber \\
    %                                       & & + (2.625 - x_{1} + x_{1}x_{2}^{3})^{2} \nonumber
    f_{10}(\textbf{x}) &=& (1.5 - x_{1} + x_{1}x_{2})^{2} + (2.25 - x_{1} + x_{1}x_{2}^2)^{2}  \nonumber \\
                                           & & + (2.625 - x_{1} + x_{1}x_{2}^{3})^{2} \nonumber
\end{eqnarray}
subject to  $-4.5 \leq x_{i} \leq 4.5$.  The global minimum is located at $\textbf{x}^{*}=(3,0.5)$, $f(\textbf{x}^{*}) = 0 $. \\

%The global minima is located at $\textbf{x} = f(3,0.5) = 0$ \\

%% Biggs EXP2 Function

\item \textbf{Biggs EXP2 Function} \cite{BIGGS1971} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{11}(\textbf{x}) &=& \sum_{i=1}^{10} \left(e^{-t_{i}x_{1}} - 5e^{-t_{i}x_{2}} - y_{i} \right)^2 \nonumber
\end{eqnarray}
where $t_{i} = 0.1i$, $y_{i}=e^{-t_{i}} - 5e^{10t_{i}}$.  It is subject to  $0 \leq x_{i} \leq 20$.
The global minimum is located at $\textbf{x}^{*}=(1,10)$, $f(\textbf{x}^{*}) = 0 $. \\

\item \textbf{Biggs EXP3 Function} \cite{BIGGS1971} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{12}(\textbf{x}) &=& \sum_{i=1}^{10} \left(e^{-t_{i}x_{1}} - x_{3}e^{-t_{i}x_{2}} - y_{i} \right)^2 \nonumber
\end{eqnarray}
where $t_{i} = 0.1i$, $y_{i}=e^{-t_{i}} - 5e^{10t_{i}}$.  It is subject to  $0 \leq x_{i} \leq 20$.
The global minimum is located at $\textbf{x}^{*}=(1,10,5)$, $f(\textbf{x}^{*}) = 0 $. \\

\item \textbf{Biggs EXP4 Function} \cite{BIGGS1971} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{13}(\textbf{x}) &=& \sum_{i=1}^{10} \left(x_{3}e^{-t_{i}x_{1}} - x_{4}e^{-t_{i}x_{2}} - y_{i} \right)^2 \nonumber
\end{eqnarray}
where $t_{i} = 0.1i$, $y_{i}=e^{-t_{i}} - 5e^{10t_{i}}$.  It is subject to  $0 \leq x_{i} \leq 20$.
The global minimum is located at $\textbf{x}^{*}=(1,10,1,5)$, $f(\textbf{x}^{*}) = 0 $. \\

\item \textbf{Biggs EXP5 Function} \cite{BIGGS1971} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{14}(\textbf{x}) &=& \sum_{i=1}^{11} \left(x_{3}e^{-t_{i}x_{1}} - x_{4}e^{-t_{i}x_{2}} + 3e^{-t_{i}x_{5}} - y_{i} \right)^2 \nonumber
\end{eqnarray}
where $t_{i} = 0.1i$, $y_{i}=e^{-t_{i}} - 5e^{10t_{i}} + 3e^{-4t_{i}}$.  It is subject to  $0 \leq x_{i} \leq 20$.
The global minimum is located at $\textbf{x}^{*}=(1,10,1,5,4)$, $f(\textbf{x}^{*}) = 0 $. \\

\item \textbf{Biggs EXP5 Function} \cite{BIGGS1971} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{15}(\textbf{x}) &=& \sum_{i=1}^{13} \left(x_{3}e^{-t_{i}x_{1}} - x_{4}e^{-t_{i}x_{2}} + x_{6}e^{-t_{i}x_{5}} - y_{i} \right)^2 \nonumber
\end{eqnarray}
where $t_{i} = 0.1i$, $y_{i}=e^{-t_{i}} - 5e^{10t_{i}} + 3e^{-4t_{i}}$.  It is subject to  $-20 \leq x_{i} \leq 20$.
The global minimum is located at $\textbf{x}^{*}=(1,10,1,5,4,3)$, $f(\textbf{x}^{*}) = 0 $. \\

\item \textbf{Bird Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{16}(\textbf{x}) &=&  \textrm{sin}(x_{1})e^{(1 - \textrm{cos}(x_{2}))^2} + \textrm{cos}(x_{2})e^{(1 - \textrm{sin}(x_{1}))^2}+ (x_{1} - x_{2})^2 \nonumber
\end{eqnarray}
subject to  $-2\pi \leq x_{i} \leq 2\pi$.  The global minimum is located at $\textbf{x}^{*}=(4.70104$, $3.15294)$,$(-1.58214$, $-3.13024)$,
$f(\textbf{x}^{*}) = -106.764537 $. \\

%% BOHACHEVSKY Function 1
\item \textbf{Bohachevsky 1 Function} \cite{BOHACHEVSKY1986} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	   f_{17}(\textbf{x}) &=& x_{1}^{2} + 2x_{2}^{2} - 0.3\textrm{cos}(3 \pi x_{1}) \nonumber \\
                                           & & - 0.4\textrm{cos}(4 \pi x_{2}) + 0.7  \nonumber
\end{eqnarray}
    subject to  $-100 \leq x_{i} \leq 100$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$,
    $f(\textbf{x}^{*}) = 0$.\\

%% BOHACHEVSKY Function 2
\item \textbf{Bohachevsky 2 Function} \cite{BOHACHEVSKY1986} (Continuous, Differentiable, Non-separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	    f_{18}(\textbf{x}) &=& x_{1}^{2} + 2x_{2}^{2} - 0.3\textrm{cos}(3 \pi x_{1})\cdot0.4\textrm{cos}(4 \pi x_{2}) \nonumber \\
                                           & &  + 0.3  \nonumber
\end{eqnarray}
    subject to  $-100 \leq x_{i} \leq 100$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$,
    $f(\textbf{x}^{*}) = 0$.\\

%% BOHACHEVSKY Function 3
\item \textbf{Bohachevsky 3 Function} \cite{BOHACHEVSKY1986} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{19}(\textbf{x}) &=& x_{1}^{2} + 2x_{2}^{2} -0.3\textrm{cos}(3 \pi x_{1} + 4 \pi x_{2}) + 0.3 \nonumber
\end{eqnarray}
    subject to  $-100 \leq x_{i} \leq 100$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$,
    $f(\textbf{x}^{*}) = 0$.\\

%% BOOTH FUNCTION
\item \textbf{Booth Function} (Continuous, Differentiable, Non-separable, Non-Scalable, Unimodal) %% Check the modality
\begin{eqnarray}
	   f_{20}(\textbf{x}) &=& (x_{1} + 2x_{2} - 7)^{2} + (2x_{1} + x_{2} - 5)^{2}\nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f(1,3)$,
$f(\textbf{x}^{*}) = 0$.\\

%%%%%%%%%%%%%%%%%%%
%BOX-BETTS (MVF)
%%%%%%%%%%%%%%%%%%
\item \textbf{Box-Betts Quadratic Sum Function} \cite{ALI2005} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{21}(\textbf{x}) &=& \sum_{i=0}^{D-1}g(x_{i})^2 \nonumber \\
           \textrm{where} \nonumber \\
                                      g(x) &=& e^{-0.1(i + 1)x_{1}} - e^{-0.1(i + 1)x_{2}} -  e^{[(-0.1(i + 1)) - e^{-(i + 1)}]x_{3}} \nonumber
\end{eqnarray}
subject to  $0.9 \leq x_{1} \leq 1.2$, $9 \leq x_{2} \leq 11.2$, $0.9 \leq x_{2} \leq 1.2$.  The global minimum is located at $\textbf{x}^{*} = f(1,10,1)$
$f(\textbf{x}^{*}) = 0$.  \\

%% BRANIN FUNCTION
\item \textbf{Branin RCOS Function} \cite{BRANIN1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{22}(\textbf{x}) &=& \left(x_2 - \frac{5.1 x_1^2}{4 \pi ^2} + \frac{5 x_1}{\pi}- 6 \right)^2 \nonumber \\
                                    & & + 10 \left(1 - \frac{1}{8 \pi} \right) \cos(x_1)  + 10 \nonumber
\end{eqnarray}
with domain $-5 \leq x_1 \le 10$, $0 \leq x_1 \leq 15$. It has three global minima at $\textbf{x}^{*} = f(\{-\pi, 12.275\}, \{\pi, 2.275\}, \{3\pi, 2.425\})$,
$f(\textbf{x}^{*}) = 0.3978873$.  \nonumber \\

\item \textbf{Branin RCOS 2 Function} \cite{MUNTEANU1998} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{23}(\textbf{x}) &=& \left(x_2 - \frac{5.1 x_1^2}{4 \pi ^2} + \frac{5 x_1}{\pi}- 6 \right)^2 \nonumber \\
                       & & + 10 \left(1 - \frac{1}{8 \pi} \right) \cos(x_1)\cos(x_2)  \ln(x_{1}^{2} + x_{2}^{2} + 1)+ 10 \nonumber
\end{eqnarray}
with domain $-5 \leq x_i \le 15$.  The global minimum is located at $\textbf{x}^{*} = f(-3.2, 12.53)$,
$f(\textbf{x}^{*}) = 5.559037$.  \nonumber \\

\item \textbf{Brent Function} \cite{BRANIN1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    f_{24}(\textbf{x}) &=& \left(x_1 + 10\right)^2 + \left(x_2 + 10\right)^2 + e^{-x_{1}^2 - x_{2}^{2}}
\end{eqnarray}
with domain $-10 \leq x_i \le 10$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$,
$f(\textbf{x}^{*}) = 0$.  \nonumber \\

%%%%%%%%%%%%%%%%%%
%%BROWN FUNCTION (PSOS)
%%%%%%%%%%%%%%%%%%

\item \textbf{Brown Function} \cite{BEGAMBRE2009} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{25}(\textbf{x}) &=& \sum_{i=1}^{n-1}(x_{i}^{2})^{(x_{i+1}^{2} + 1)} + (x_{i+1}^{2})^{(x_{i}^{2} + 1)} \nonumber
\end{eqnarray}
subject to  $-1 \leq x_{i} \leq 4$.  The global minimum is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0$.  \\

%%%%%%%%%%%%%%%%%
%%BUKIN-2 FUNCTION (PSOS)
%%%%%%%%%%%%%%%%%%
Bukin functions \cite{SILAGADZE2007} are almost fractal (with fine seesaw edges) in the surroundings of their minimal points.
Due to this property, they are extremely difficult to optimize  by  any  global or local optimization methods.

\item \textbf{Bukin 2 Function} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{26}(\textbf{x}) &=& 100(x_{2} - 0.01x_{1}^2 + 1) + 0.01(x_{1} + 10)^2  \nonumber
\end{eqnarray}
subject to  $-15 \leq x_{1} \leq -5$ and $-3 \leq x_{2} \leq -3$.  The global minimum is located at $\textbf{x}^{*} = f(-10,0)$,
$f(\textbf{x}^{*}) = 0$.  \\

%%%%%%%%%%%%%%%%%%
%%BUKIN-4 FUNCTION (PSOS)
%%%%%%%%%%%%%%%%%%
\item \textbf{Bukin 4 Function} (Continuous, Non-Differentiable, Separable, Non-scalable, Multimodal)
\begin{eqnarray}
	       f_{27}(\textbf{x}) &=& 100x_{2}^2 + 0.01\|x_{1} + 10\|  \nonumber
\end{eqnarray}
subject to  $-15 \leq x_{1} \leq -5$ and $-3 \leq x_{2} \leq -3$.  The global minimum is located at $\textbf{x}^{*} = f(-10,0)$,
$f(\textbf{x}^{*}) = 0$.  \\

%%%%%%%%%%%%%%%%%%
%%BUKIN-6 FUNCTION (PSOS)
%%%%%%%%%%%%%%%%%%

\item \textbf{Bukin 6 Function} (Continuous, Non-Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{28}(\textbf{x}) &=& 100\sqrt{\|x_{2} - 0.01x_{1}^2\|} + 0.01\|x_{1} + 10 \|  \nonumber
\end{eqnarray}
subject to  $-15 \leq x_{1} \leq -5$ and $-3 \leq x_{2} \leq -3$.  The global minimum is located at $\textbf{x}^{*} = f(-10,1)$,
$f(\textbf{x}^{*}) = 0$.\\

%% THREE-HUMP CAMEL FUNCTION
\item \textbf{Camel Function -- Three Hump} \cite{BRANIN1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{29}(\textbf{x}) &=&  2x_{1}^{2} - 1.05x_{1}^{4} + x_{1}^6/6 + x_{1}x_{2} + x_{2}^{2} \nonumber
\end{eqnarray}
    subject to  $-5 \leq x_{i} \leq 5$.  The global minima is located at $\textbf{x}^{*} = f(0,0)$, $f(\textbf{x}^{*}) = 0$.

%% 3-HUMP CAMEL FUNCTION
\item \textbf{Camel Function -- Six Hump} \cite{BRANIN1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{30}(\textbf{x}) &=&  (4 - 2.1x_{1}^{2} + \frac{x_{1}^{4}}{3})x_{1}^{2} \nonumber \\
                                           & &  + x_{1}x_{2} + (4x_{2}^{2} - 4)x_{2}^{2} \nonumber
\end{eqnarray}
    subject to  $-5 \leq x_{i} \leq 5$.  The two global minima are located at $\textbf{x}^{*}$ = $f(\{-0.0898, 0.7126\}$, $\{0.0898, -0.7126, 0\})$,
     $f(\textbf{x}^{*}) = -1.0316$.

\item \textbf{Chen Bird Function} \cite{CHEN2003} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{31}(\textbf{x}) &=& -\frac{0.001}{\bigl \lfloor{(0.001)^2 + (x_1 - 0.4x_2 - 0.1)^2}\bigr \rfloor} - \nonumber \\
                       & & \frac{0.001}{\bigl \lfloor{(0.001)^2 + (2x_1 + x_2 - 1.5)^2} \bigr \rfloor}  \nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$ The global minimum is located at $\textbf{x}^{*} = f(-\frac{7}{18}, -\frac{13}{18})$,
$f(\textbf{x}^{*}) = -2000$.\\


\item \textbf{Chen V Function} \cite{CHEN2003} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{32}(\textbf{x}) &=& -\frac{0.001}{\bigl \lfloor{(0.001)^2 + (x_1^2 + x_2^2 - 1)^2}\bigr \rfloor} - \nonumber \\
                       & &  \frac{0.001}{\bigl \lfloor{(0.001)^2 + (x_1^2 + x_2^2 - 0.5)^2}\bigr \rfloor} - \nonumber \\
                       & &  \frac{0.001}{\bigl \lfloor{(0.001)^2 + (x_1^2 - x_2^2)^2}\bigr \rfloor}         \nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$ The global minimum is located at $\textbf{x}^{*}$ = $f(-\-0.3888889$, $0.7222222)$,
$f(\textbf{x}^{*}) = -2000$.\\


\item \textbf{Chichinadze Function} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{33}(\textbf{x})  &=& x_{1}^{2} - 12x_{1} + 11 + \nonumber \\
                        & & 10\textrm{cos}(\pi x_{1}/2) + 8\textrm{sin}(5\pi x_{1}/2) - \nonumber \\
                        & & (1/5)^{0.5}\exp(-0.5(x_{2} - 0.5){^2}) \nonumber
\end{eqnarray}
subject to  $-30 \leq x_{i} \leq 30$.  The global minimum is located at $\textbf{x}^{*} = f(5.90133, 0.5) $,
    $f(\textbf{x}^{*}) = -43.3159$.  \\

\item \textbf{Chung Reynolds Function} \cite{CHUNG1998} (Continuous, Differentiable, Partially-Separable, Scalable, Unimodal)
\begin{eqnarray}
    f_{34}(\textbf{x})  &=& \bigl(\sum_{i=1}^{D}x_{i}^2\bigr)^2 \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$.  The global minimum is located at $\textbf{x}^{*} = f(0,\cdots,0) $,
    $f(\textbf{x}^{*}) = 0$.  \\

%% COLA FUNCTION
\item \textbf{Cola Function} \cite{ADORIO2005} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)

The 17-dimensional function computes indirectly the
formula $(D,u)$  by setting $x_0 = y_0, x_1 = u_0, x_i = u_{2(i-2)},
y_i = u_{2(i-2)+1}$
$$
    f_{35}(n, u) = h(x,y) = \sum_{j<i} (r_{i,j} - d_{i,j}) ^2
$$
where $r_{i,j}$ is given by
$$
    r_{i,j} = [ (x_i-x_j)^2 + (y_i - y_j)^2 ]^{1/2}
$$
and $d$ is a symmetric matrix given by
$$
\textbf{d} = [d_{ij}]= \left(
\begin{array}{llllllllll}
  1.27 \\
  1.69 &1.43 \\
  2.04 &2.35 &2.43 \\
  3.09 &3.18 &3.26 &2.85 \\
  3.20 &3.22 &3.27 &2.88 &1.55 \\
  2.86 &2.56 &2.58 &2.59 &3.12 &3.06 \\
  3.17 &3.18 &3.18 &3.12 &1.31 &1.64 &3.00 \\
  3.21 &3.18 &3.18 &3.17 &1.70 &1.36 &2.95 &1.32\\
  2.38 &2.31 &2.42 &1.94 &2.85 &2.81 &2.56 &2.91 &2.97 \\
\end{array}
\right)
$$
This function has bounds $0 \le x_0 \le 4$ and $-4 \le x_i \le 4$ for
$i = 1 \ldots D-1$. It has a global minimum of $f(\textbf{x}^{*}) = 11.7464$. \\

%%%%%%%%%%%%%%%%%%%%%%
%%COLVILLE FUNCTION (MVF)
%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Colville Function} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)   %% check the modality
\begin{eqnarray}
	       f_{36}(\textbf{x}) &=& 100(x_{1} - x_{2}^{2})^{2} + (1 - x_{1})^{2} + \nonumber \\
                                           & & 90(x_{4} - x_{3}^{2})^{2} + (1 - x_{3})^{2}  + \nonumber \\
                                           & & 10.1((x_{2} - 1)^{2} + (x_{4} - 1)^{2}) + \nonumber \\
                                           & & 19.8(x_{2} - 1)(x_{4} - 1) \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(1,\cdots,1)$, $f(\textbf{x}^{*}) = 0$.  \\

%% CORANA FUNCTION

\item \textbf{Corana Function} \cite{CORANA1987} (Discontinuous, Non-Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
        %\mathop {\min }\limits_x f(x) = \sum\limits_{i = 0}^{D - 1}
        f_{37}(\textbf{x}) =
        {\left\{
            \begin{array}{l}
                0.15\left( {{z_i} - 0.05{\mathop{\rm sgn}} {{\left( {{z_i}} \right)}^2}} \right){d_i}{\rm{~ ~if }}\left| {{v_i}} \right| < A \nonumber \\
                {d_i}x_i^2{\rm{~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ otherwise}} \nonumber
            \end{array} \right.}
\end{eqnarray}
where
\begin{eqnarray}
    v_{i} &=& \left|x_{i} - z_{i} \right|, ~ ~ A = 0.05 \nonumber \\
    z_{i} &=& 0.2\left\lfloor {\left| {\frac{{{x_{i}}}}{{0.2}}} \right| + 0.49999} \right\rfloor {{\rm sgn}} \left( {{x_{i}}} \right) \nonumber \\
    d_{i} &=& (1,1000,10,100)
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f(0,0,0,0)$,
$f(\textbf{x}^{*}) = 0$.  \\

%%%%%%%%%%%%%%%%%%
%% COSINE MIXTURE
\item \textbf{Cosine Mixture Function} \cite{ALI2005} (Discontinuous, Non-Differentiable, Separable, Scalable, Multimodal)
        \begin{eqnarray}
	       f_{38}(\textbf{x}) &=& -0.1\sum_{i=1}^{n}\textrm{cos}(5 \pi x_{i}) - \sum_{i=1}^{n}x_{i}^{2} \nonumber
        \end{eqnarray}
    subject to  $-1 \leq x_{i} \leq 1$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$,
    $f(\textbf{x}^{*}) = (0.2 \, \textrm{or} \, 0.4) \, \textrm{for} \, \, \textrm{n} = 2 \, \textrm{and} \, 4$
    respectively.  \\

%% CROSS-IN-TRAY
\item \textbf{Cross-in-Tray Function} \cite{MISHRA2006_6} (Continuous, Non-Separable, Non-Scalable, Multimodal)
        \begin{eqnarray}
	       f_{39}(\textbf{x}) &=& -0.0001[|\textrm{sin}(x_{1})\textrm{sin}(x_{2})  \nonumber \\
                                           & & e^{|100 - [(x_{1}^{2} + x_{2}^{2})]^{0.5}/\pi|}| + 1]^{0.1} \nonumber
        \end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.

    The four global minima are located at $\textbf{x}^{*}$ =
    $f(\pm 1.349406685353340$, $\pm 1.349406608602084)$,
    $f(\textbf{x}^{*}) = -2.06261218 $. \\

%% CSENDES FUNCTION
\item \textbf{Csendes Function} \cite{CSENDES1997} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{40}(\textbf{x}) &=& \sum_{i=1}^D x_{i}^6\left(2 + \sin\frac{1}{x_{i}}\right) \nonumber
\end{eqnarray}
    subject to  $-1 \leq x_{i} \leq 1$.  The global minimum is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
    $f(\textbf{x}^{*}) = 0$.  \\

\item \textbf{Cube Function} \cite{LAVI1966} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    f_{41}(\textbf{x}) &=& 100\left(x_2 - x_{1}^3\right)^2 + (1 - x_{1})^2 \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f(-1,1)$,
    $f(\textbf{x}^{*}) = 0 $. \\

\item \textbf{Damavandi Function} \cite{DAMAVANDI2005} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
        \begin{eqnarray}
	       f_{42}(\textbf{x}) &=& \left[1 - {\left|{\frac{\textrm{sin}[\pi(x_{1} - 2)]\textrm{sin}[\pi(x_{2} - 2)]}{\pi^2(x_{1} - 2)(x_{2}-2)}}\right|}^5\right]  \nonumber \\
                                           & & \left[2 + (x_{1} - 7)^{2} + 2(x_{2} - 7 )^{2}\right] \nonumber
        \end{eqnarray}
    subject to  $0 \leq x_{i} \leq 14$.  The global minimum is located at $\textbf{x}^{*} = f(2,2)$,
    $f(\textbf{x}^{*}) = 0$. \\

%%DEB 1
\item \textbf{Deb 1 Function} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{43}(\textbf{x}) &=& -\frac{1}{D}\sum_{i=1}^{D}\textrm{sin}^{6}(5\pi x_{i}) \nonumber
        \end{eqnarray}
    subject to  $-1 \leq x_{i} \leq 1$.  The number of global minima is $5^{D}$ that are evenly spaced in the function landscape,
    where $D$ represents the dimension of the problem. \\

%%DEB 3
\item \textbf{Deb 3 Function} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{44}(\textbf{x}) &=& -\frac{1}{D}\sum_{i=1}^{D}\textrm{sin}^{6}(5\pi(x_{i}^{3/4} - 0.05)) \nonumber
        \end{eqnarray}
    subject to  $-1 \leq x_{i} \leq 1$.  The number of global minima is $5^{D}$ that are unevenly spaced in the function landscape,
    where $D$ represents the dimension of the problem. \\

%% DECKKERS-AARTS Function
\item \textbf{Deckkers-Aarts Function} \cite{ALI2005} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{45}(\textbf{x}) &=& 10^{5}x_{1}^{2} + x_{2}^{2} - (x_{1}^{2} + x_{2}^{2})^{2} +
                                            10^{-5}(x_{1}^{2} + x_{2}^{2})^{4} \nonumber
        \end{eqnarray}
    subject to  $-20 \leq x_{i} \leq 20$.  The two global minima are located at $\textbf{x}^{*} = f(0, \pm 15)$
    $f(\textbf{x}^{*}) = -24777 $. \\

\item \textbf{deVilliers Glasser 1 Function} \cite{deVILLERS1981}(Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{46}(\textbf{x}) &=& \sum_{i=1}^{24}\left[x_{1}x_{2}^{t_{i}} \sin(x_{3}t_{i} + x_{4}) - y_{i}\right]^2 \nonumber
\end{eqnarray}
where $t_{i} = 0.1(i - 1)$, $y_{i} = 60.137\times1.371^{t_{i}}\sin(3.112t_{i} + 1.761)$.  It is
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is $f(\textbf{x}^{*}) = 0 $. \\

\item \textbf{deVilliers Glasser 2 Function} \cite{deVILLERS1981} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{47}(\textbf{x}) &=& \sum_{i=1}^{16}\left[x_{1}x_{2}^{t_{i}} \tanh\left[x_{3}t_{i} + \sin(x_{4}t_{i})\right]\cos(t_{i}e^{x_{5}}) - y_{i}\right]^2 \nonumber
\end{eqnarray}
where $t_{i} = 0.1(i - 1)$, $y_{i} = 53.81\times1.27^{t_{i}}\tanh(3.012t_{i} + \sin(2.13t_{i}))\cos(e^{0.507}t_{i})$.  It is
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is $f(\textbf{x}^{*}) = 0 $. \\

%% DIXON-PRICE FUNCTION
%% http://thome.postech.ac.kr/user/informatics/paper/200705_A%20novel%20three-phase%20trajectory%20informed%20search.pdf
%% A Novel three-phase trajectory infomed search methodology for GO
\item \textbf{Dixon \& Price Function} \cite{DIXON1989} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
    f_{48}(\textbf{x}) &=& (x_{1} - 1)^2 + \sum_{i=2}^{D}i(2x_{i}^2 - x_{i-1})^2 \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f(2^(\frac{2^i-2}{2^i}))$,
$f(\textbf{x}^{*}) = 0$.  \\

\item \textbf{Dolan  Function} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{49}(\textbf{x}) &=& (x_{1} + 1.7x_{2})\sin(x_{1}) - 1.5x_{3} - 0.1x_{4}\cos(x_{4} + x_{5} - x_{1}) + \nonumber \\
                              & & 0.2x_{5}^{2} - x_{2} - 1 \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$.  The global minimum is $f(\textbf{x}^{*}) = 0 $. \\

%% EASOM FUNCTION (OPPOSITION BASED DIFFERENTIAL EVOLUTION)
\item \textbf{Easom Function} \cite{CHUNG1998}(Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{50}(\textbf{x}) &=& -\textrm{cos}(x_{1})\textrm{cos}(x_{2})\exp[-(x_{1} - \pi)^{2} \nonumber \\
                                           & & - (x_{2} - \pi)^{2}] \nonumber
\end{eqnarray}
    subject to  $-100 \leq x_{i} \leq 100$.  The global minimum is located at $\textbf{x}^{*} = f(\pi, \pi)$, $f(\textbf{x}^{*}) = -1 $. \\

\item \textbf{El-Attar-Vidyasagar-Dutta Function} \cite{EL-ATTAR1979} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
	       f_{51}(\textbf{x}) &=& (x_{1}^{2} + x_{2} - 10)^2 + (x_{1} + x_{2}^{2} - 7)^2  + \nonumber\\
                              & & (x_{1}^{2} + x_{2}^{3} - 1)^2 \nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f(2.842503, 1.920175)$,
$f(\textbf{x}^{*}) = 0.470427 $. \\

%% EGG-CRATE FUNCTION (Introduction to Mathematical Optimization -- From Linear Programming to Meta-heuristics)
\item \textbf{Egg Crate Function} (Continuous, Separable, Non-Scalable)
\begin{eqnarray}
    f_{52}(\textbf{x}) &=& x_{1}^{2} + x_{2}^{2} + 25(\textrm{sin}^{2}(x_{1}) + \textrm{sin}^{2}(x_{2})) \nonumber
\end{eqnarray}
    subject to  $-5 \leq x_{i} \leq 5$.  The global minimum is located at $\textbf{x}^{*} = f(0, 0)$,
$f(\textbf{x}^{*}) = 0$.\\

%% EGG-HOLDER FUNCTION (Some new Test Problems for global optimization and performance of RPS MISHRA, 23.08.2006)
\item \textbf{Egg Holder Function} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{53}(\textbf{x}) &=& \sum_{i=1}^{m-1} [-(x_{i+1} + 47)\textrm{sin}\sqrt{|x_{i+1} + x_{i}/2 + 47|}  \nonumber \\
                                           & & - x_{i}\textrm{sin}\sqrt{|x_{i} -( x_{i+1} + 47)|} ] \nonumber
        \end{eqnarray}
    subject to  $-512 \leq x_{i} \leq 512$.  The global minimum is located at $\textbf{x}^{*} = f(512, 404.2319)$,
    $f(\textbf{x}^{*}) \approx 959.64 $.\\

%%%%%%%%%%%%%%%%%%%%%%
% EXPONENTIAL FUNCTION
%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Exponential Function} \cite{RAHNAMAYAN2007_1} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
     f_{54}(\textbf{x}) &=&  - \exp \left( { - 0.5\sum\limits_{i = 1}^D {x_i^2} } \right) \nonumber	
\end{eqnarray}
    subject to  $-1 \leq x_{i} \leq 1$.  The global minima is located at $\textbf{x} = f(0,\cdots,0)$,
    $f(\textbf{x}^{*}) = 1$.  \\

%% EXPONENTIAL-2 FUNCTION
\item \textbf{Exp 2 Function} \cite{ADORIO2005} (Separable)
    \begin{eqnarray}
        f_{55}(\textbf{x}) &=& \sum_{i=0}^9\left( e^{-i x_1 / 10} - 5 e^{-i x_2 / 10} -  e^{-i / 10} \nonumber
        + 5  e^{-i} \right)^2
        \end{eqnarray}
    with domain $0 \leq x_{i} \le 20$.   The global minimum is located at $\textbf{x}^{*} = f(1,10)$,
    $f(\textbf{x}^{*}) = 0$.\\

%% FREUDENSTEIN-ROTH ()
\item \textbf{Freudenstein Roth Function} \cite{RAO2009} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{56}(\textbf{x}) &=& (x_{1} - 13 + ((5-x_{2})x_{2}-2)x_{2})^{2} + \nonumber \\
                                           & & (x_{1} - 29 + ((x_{2} + 1)x_{2} - 14)x_{2})^{2} \nonumber
\end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f(5,4)$,
    $f(\textbf{x}^{*}) = 0$. \\

%% GIUNTA FUNCTION (Mishra)
\item \textbf{Giunta Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{57}(\textbf{x}) &=& 0.6 + \sum_{i=1}^{2}[\textrm{sin}(\frac{16}{15}x_{i} - 1)  \nonumber \\
                                          & &  + \textrm{sin}^{2}(\frac{16}{15}x_{i} - 1) \nonumber \\
                                          & &  + \frac{1}{50}\textrm{sin}(4(\frac{16}{15}x_{i} - 1))] \nonumber
\end{eqnarray}
subject to  $-1 \leq x_{i} \leq 1$.  The global minimum is located at $\textbf{x}^{*} = f(0.45834282,0.45834282)$,
$f(\textbf{x}^{*}) = 0.060447 $. \\

%%GOLD-STEIN PRICE FUNCTION
\item \textbf{Goldstein Price Function} \cite{GOLDSTEIN1971} (Continuous, Differentiable, Non-separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{58}(\textbf{x}) &=& [1  + (x_{1} + x_{2} + 1)^{2}(19 - 14x_{1}  \nonumber \\
    & & +  3x_{1}^{2} - 14x_{2} +  6x_{1}x_{2} +  3x_{2}^{2})] \nonumber \\
    & & \times [30 + (2x_{1} - 3x_{2})^{2} \nonumber \\
    & & (18 - 32x_{1} + 12x_{1}^{2} + 48x_{2} - 36x_{1}x_{2} + 27x_{2}^{2})] \nonumber
\end{eqnarray}
subject to  $-2 \leq x_{i} \leq 2$.  The global minimum is located at $\textbf{x}^{*} = f(0,-1)$,
$f(\textbf{x}^{*}) = 3 $. \\

%%GRIEWANK
\item \textbf{Griewank Function} \cite{GRIEWANK1981} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
    \begin{eqnarray}
	       f_{59}(\textbf{x}) &=& \sum_{i=1}^{n}\frac{x_{i}^{2}}{4000} - \prod\textrm{cos}(\frac{x_{i}}{\sqrt{i}}) + 1 \nonumber
    \end{eqnarray}
    subject to  $-100 \leq x_{i} \leq 100$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
    $f(\textbf{x}^{*}) = 0$. \\

%%%%%%%%%%%%%%%%%%%%%%%%
% GULF RESEARCH PROBLEM
%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Gulf Research Problem} \cite{SHANNO1970} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
     f_{60}(\textbf{x}) = {\sum\limits_{i = 1}^{99} {\left[ {\exp \left( { - \frac{{{{\left( {{u_i} - {x_2}} \right)}^{{x_3}}}}}{{{x_i}}}} \right) - 0.01i} \right]} ^2} \nonumber
\end{eqnarray}

where $u_{i}=25 +[-50\ln(0.01i)]^{1/1.5}$ subject to $0.1 \leq x_{1} \leq 100$, $0 \leq x_{2} \leq 25.6$ and $0 \leq x_{1} \leq 5$.  The global minimum is located at
$\textbf{x}^{*} = f(50, 25, 1.5)$, $f(\textbf{x}^{*}) = 0$. \\

%% HANSEN FUNCTION
\item \textbf{Hansen Function} \cite{FRALEY1989} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{61}(\textbf{x}) &=& \sum_{i}^{4}(i + 1)\textrm{cos}(ix_{1} + i + 1) \nonumber \\
                                           & & \sum_{j=0}^{4}(j+1)\textrm{cos}((j + 2)x_{2} + j + 1) \nonumber
\end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The multiple global minima are located at
    \[\textbf{x}^{*} = f( \{-7.589893, -7.708314\}, ~~\{-7.589893, -1.425128\},\]
                                                                                     \[ \{-7.589893, ~~4.858057\}, ~~\{-1.306708, -7.708314\}, \]
                                                                                     \[ \{-1.306708, ~~4.858057\}, ~~\{~~4.976478,  ~~4.858057\},\]                                                                                     \[ \{~~4.976478, -1.425128\},  ~~\{~~4.976478, -7.708314\}), \]
%%%%%%%%%%%%%%%%%%%%%%
% HARTMAN3 FUNCTION
%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Hartman 3 Function} \cite{HARTMAN1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{62}(\textbf{x}) &=&   - \sum\limits_{i = 1}^4 {{c_i}\exp \left[ { - \sum\limits_{j = 1}^3 {{a_{ij}}{{\left( {{x_j} - {p_{ij}}} \right)}^2}} } \right]} \nonumber
\end{eqnarray}
subject to  $0 \leq x_{j} \leq 1$, $j \in \{1,2,3\}$ with constants $a_{ij}$, $p_{ij}$ and $c_{i}$ are given as \\

%$A = \left( {\begin{smallmatrix}
%3&{10}&{30}\\
%{0.1}&{10}&{35}\\
%3&{10}&{30}\\
%{0.1}&{10}&{35}
%\end{smallmatrix}} \right)$,

$\textbf{A} = [A_{ij}] = \left( {\begin{matrix}
3&{10}&{30}\\
{0.1}&{10}&{35}\\
3&{10}&{30}\\
{0.1}&{10}&{35}
\end{matrix}} \right)$, $\textbf{\underline{c}} = {c_i} = \left[ {\begin{matrix}
1\\
{1.2}\\
3\\
{3.2}
\end{matrix}} \right]$, \\
$\textbf{\underline{p}} = {p_i} = \left( {\begin{matrix}
{0.3689}&{0.1170}&{0.2673}\\
{0.4699}&{0.4837}&{0.7470}\\
{0.1091}&{0.8732}&{0.5547}\\
{0.03815}&{0.5743}&{0.8828}
\end{matrix}} \right)$  \\

The global minimum is located at $\textbf{x}^{*} = f(0.1140, 0.556, 0.852)$,
$f(\textbf{x}^{*})\approx -3.862782 $. \\

%%%%%%%%%%%%%%%%%%%%%%
% HARTMAN6 FUNCTION
%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Hartman 6 Function} \cite{HARTMAN1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{63}(\textbf{x}) &=&  - \sum\limits_{i = 1}^4 {{c_i}\exp \left[ { - \sum\limits_{j = 1}^6 {{a_{ij}}{{\left( {{x_j} - {p_{ij}}} \right)}^2}} } \right]} \nonumber
\end{eqnarray}
subject to  $0 \leq x_{j} \leq 1$, $j \in \{1,\cdots,6\}$ with constants $a_{ij}$, $p_{ij}$ and $c_{i}$ are given as \\

$\textbf{A} = [A_{ij}] = \left( {\begin{matrix}
{10}&3&{17}&{3.5}&{1.7}&8\\
{0.05}&{10}&{17}&{0.1}&8&{14}\\
3&{3.5}&{1.7}&{10}&{17}&8\\
{17}&8&{0.05}&{10}&{0.1}&{14}
\end{matrix}} \right)$, $\textbf{\underline{c}} = {c_i} = \left[ {\begin{matrix}
1\\
{1.2}\\
3\\
{3.2}
\end{matrix}} \right]$  \\
%\\ \\
$\textbf{\underline{p}} = {p_i} = \left( {\begin{matrix}
\small{0.1312}&{0.1696}&{0.5569}&{0.0124}&{0.8283}&{0.5586}\\
{0.2329}&{0.4135}&{0.8307}&{0.3736}&{0.1004}&{0.9991}\\
{0.2348}&{0.1451}&{0.3522}&{0.2883}&{0.3047}&{0.6650}\\
{0.4047}&{0.8828}&{0.8732}&{0.5743}&{0.1091}&{0.0381}
\end{matrix}} \right)$ \\

The global minima is located at
$\textbf{x} = f(0.201690, 0.150011, 0.476874,0.275332, ...\\
0.311652, 0.657301)$,
$f(\textbf{x}^{*}) \approx -3.32236 $. \\
%%%%%%%%%%%%%%%%%%%%%%%%
% HELICAL VALLEY
%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Helical Valley} \cite{FLETCHER1963} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{64}(\textbf{x}) &=& 100\left[ {{{({x_2} - 10\theta )}^2} + \left( {\sqrt {x_1^2 + x_2^2}  - 1} \right)} \right] \nonumber \\
                                    & & + x_3^2 \nonumber
    \end{eqnarray}
where
\begin{eqnarray}
    \theta  = \left\{ \begin{array}{l}
\frac{1}{{2\pi }}{\tan ^{ - 1}}\left( {\frac{{{x_1}}}{{{x_2}}}} \right),{\rm{~ ~ ~ ~ ~ ~ ~ ~ ~ ~if }}~{x_1} \ge 0 \nonumber\\
\frac{1}{{2\pi }}{\tan ^{ - 1}}\left( {\frac{{{x_1}}}{{{x_2}}} + 0.5} \right){\rm{~ ~ ~ ~ if }}~{x_1} < 0
\end{array} \right.
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(1,0,0)$,  $f(\textbf{x}^{*}) = 0 $. \\

%% HIMMELBLAU
\item \textbf{Himmelblau Function} \cite{HIMMELBLAU1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
    \begin{eqnarray}
        f_{65}(\textbf{x}) &=& (x_{1}^{2} + x_{2} - 11)^{2} + (x_{1} + x_{2}^{2} - 7)^{2}    \nonumber
    \end{eqnarray}
    subject to  $-5 \leq x_{i} \leq 5$.  The global minimum is located at $\textbf{x}^{*} = f(3,2)$, $f(\textbf{x}^{*}) = 0 $.  \\

\item \textbf{Hosaki Function} \cite{BEKEY1974} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
        f_{66}(\textbf{x}) &=& (1 - 8x_{1} + 7x_{1}^2-7/3x_{1}^3 + 1/4x_{1}^4)x_{2}^2e^{-x_{2}} \nonumber
    \end{eqnarray}
    subject to  $0 \leq x_{1} \leq 5$ and $0 \leq x_{2} \leq 6$.
    The global minimum is located at $\textbf{x}^{*} = f(4,2)$, $f(\textbf{x}^{*}) \approx -2.3458 $. \\

%% Jennrich-Sampson Function
\item \textbf{Jennrich-Sampson Function} \cite{JENNRICH1968} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
     f_{67}(\textbf{x}) &=& {\sum\limits_{i = 1}^{10} {\left( {2 + 2i - \left( {{{\mathop{\rm e}\nolimits} ^{i{x_1}}} + {e^{i{x_2}}}} \right)} \right)} ^2} \nonumber
\end{eqnarray}
subject to $-1 \leq x_{i} \leq 1$.  The global minimum is located at $\textbf{x}^{*} = f(0.257825,0.257825)$, $f(\textbf{x}^{*}) = 124.3612 $.  \\

\item \textbf{Langerman-5 Function} \cite{BERSINI1996} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{68}(\textbf{x}) &=& -\sum_{i=1}^{m}c_{i}e^{-\frac{1}{\pi} \sum_{j=1}^{D}(x_{j} - a_{ij})^2}\textrm{cos}\left(\pi \sum_{j=1}^{D}(x_{j} - a_{ij})^2\right) \nonumber
\end{eqnarray}

subject to $ 0 \le x_j \le 10$, where $j \in [0, D-1]$ and $m=5$. It has a global minimum value of $f(\textbf{x}^{*}) = -1.4$.
The matrix $A$ and column vector $c$ are given as

The matrix $A$ is given by
{\small
$$
\textbf{{A}}=[A_{ij}] =\left[
\begin{array}{cccccccccc}
    9.681& 0.667&4.783& 9.095& 3.517& 9.325& 6.544& 0.211& 5.122& 2.020  \\
    9.400& 2.041& 3.788& 7.931& 2.882& 2.672& 3.568& 1.284& 7.033& 7.374\\
    8.025& 9.152& 5.114& 7.621& 4.564& 4.711& 2.996& 6.126& 0.734& 4.982\\
    2.196& 0.415& 5.649& 6.979& 9.510& 9.166& 6.304& 6.054& 9.377& 1.426\\
    8.074& 8.777& 3.467& 1.863& 6.708& 6.349& 4.534& 0.276& 7.633& 1.567\\
\end{array}
\right]
$$
}
$\textbf{\underline{c}}= {c_i} = \left[ {\begin{array}{rrrrr}
{0.806}\\
{0.517}\\
{1.5}\\
{0.908}\\
{0.965}
\end{array}} \right]$

% KEANE FUNCTION
\item \textbf{Keane Function} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
    \begin{eqnarray}
        f_{69}(\textbf{x}) &=& \frac{\textrm{sin}^{2}(x_{1} - x_{2})\textrm{sin}^{2}(x_{1} + x_{2})}{\sqrt{x_{1}^{2} + x_{2}^{2}}}    \nonumber
    \end{eqnarray}
    subject to  $0 \leq x_{i} \leq 10$.

    The multiple global minima are located at $\textbf{x}^{*}$ =
    $f(\{0, 1.39325\}$,$\{1.39325, 0\})$, $f(\textbf{x}^{*})$ =$ -0.673668$. \\

%% LEON FUNCTION
\item \textbf{Leon Function} \cite{LAVI1966}(Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
    \begin{eqnarray}
        f_{70}(\textbf{x}) &=& 100(x_{2} - x_{1}^{2})^2 + (1 - x_{1})^{2} \nonumber
    \end{eqnarray}
    subject to  $-1.2 \leq x_{i} \leq 1.2$.  A global minimum is located at $f(\textbf{x}^{*}) = f(1,1)$, $f(\textbf{x}^{*}) = 0$.\\


\item \textbf{Matyas Function} \cite{HEDAR} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
    \begin{eqnarray}
        f_{71}(\textbf{x}) &=& 0.26(x_{1}^2 + x_{2}^2) - 0.48x_{1}x_{2} \nonumber
    \end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$, $f(\textbf{x}^{*}) = 0 $. \\

% McCormick Function
\item \textbf{McCormick Function} \cite{LOOTSMA1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{72}(\textbf{x}) &=& \sin(x_{1} + x_{2}) + (x_{1} - x_{2})^2 - (3/2)x_{1} + (5/2)x_{2} + 1 \nonumber
\end{eqnarray}
subject to $-1.5 \leq x_{1} \leq 4$ and $-3 \leq x_{2} \leq 3$.  The global minimum is located at $\textbf{x}^{*} = f(-0.547,-1.547)$,
$f(\textbf{x}^{*}) \approx -1.9133 $. \\

%%%%%%%%%%%%%%%%%%
% MIELE-CANTRELL
%%%%%%%%%%%%%%%%%%
\item \textbf{Miele Cantrell Function} \cite{CRAGG1969} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
        f_{73}(\textbf{x}) &=& {\left( {{e^{ - {x_1}}} - {x_2}} \right)^4} + 100{\left( {{x_2} - {x_3}} \right)^6} \nonumber \\
                                        & & + {\left( {\tan \left( {{x_3} - {x_4}} \right)} \right)^4} + x_1^8 \nonumber
\end{eqnarray}
subject to  $-1 \leq x_{i} \leq 1 $.  The global minimum is located at $\textbf{x}^{*} = f(0,1,1,1)$, $f(\textbf{x}^{*}) = 0$. \\

\item \textbf{Mishra 1 Function} \cite{MISHRA2006_1} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
        f_{74}(\textbf{x}) &=& \left(1 + D - \sum_{i=1}^{N-1}x_{i}\right)^{N - \sum_{i=1}^{N-1}x_{i}}
\end{eqnarray}
subject to  $0 \leq x_{i} \leq 1 $.  The global minimum is $f(\textbf{x}^{*}) = 2$. \\


\item \textbf{Mishra 2 Function} \cite{MISHRA2006_1} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
        f_{75}(\textbf{x}) &=& \left(1 + D - \sum_{i=1}^{N-1}0.5(x_{i} + x_{i+1})\right)^{N - \sum_{i=1}^{N-1}0.5(x_{i} + x_{i+1})}
\end{eqnarray}
subject to  $0 \leq x_{i} \leq 1 $.  The global minimum is $f(\textbf{x}^{*}) = 2$. \\

\item \textbf{Mishra 3 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
        f_{76}(\textbf{x}) &=& \sqrt{\bigl\lvert {\cos{\sqrt{\bigl \lvert x_{1}^2 + x_{2}^2 \bigr\rvert}}\bigr \rvert}} + 0.01(x_{1} + x_{2}) \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f(-8.466, -10)$, $f(\textbf{x}^{*}) = -0.18467$. \\

\item \textbf{Mishra 4 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
        f_{77}(\textbf{x}) &=& \sqrt{\bigl \lvert {\sin{\sqrt{\bigl \lvert x_{1}^2 + x_{2}^2 \bigr \rvert }\bigr \rvert}}} + 0.01(x_{1} + x_{2}) \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f(-9.94112, -10)$, $f(\textbf{x}^{*}) = -0.199409$. \\

\item \textbf{Mishra 5 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
        f_{78}(\textbf{x}) &=& \Big[\sin^2(\cos((x_1) + \cos(x_2)))^2 + \cos^2(\sin(x_1) + \sin(x_2)) + x_{1} \Big]^2 \nonumber \\
                           & & + 0.01(x_{1} + x_{2}) \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f(-1.98682, -10)$, $f(\textbf{x}^{*}) = -1.01983$. \\

\item \textbf{Mishra 6 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
        f_{79}(\textbf{x}) &=& -\ln\Big[\sin^2(\cos((x_1) + \cos(x_2)))^2 - \cos^2(\sin(x_1) + \sin(x_2)) + x_{1} \Big]^2 \nonumber \\
                           & & + 0.01((x_{1} - 1)^2 + (x_{2} - 1)^2) \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f(2.88631, 1.82326)$, $f(\textbf{x}^{*}) = -2.28395$. \\

\item \textbf{Mishra 7 Function} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
        f_{80}(\textbf{x}) &=& \Big[\prod_{i=1}^{D}x_{i} - N!\Big]^2 \nonumber
\end{eqnarray}
The global minimum is $f(\textbf{x}^{*}) = 0$. \\

\item \textbf{Mishra 8 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
   f_{81}(\textbf{x}) &=& 0.001\Big[\Big|x_{1}^{10} - 20x_{1}^{9} + 180x_{1}^{8} - 960x_{1}^{7} +3360x_{1}^{6} - 8064x_{1}^{5} \nonumber\\
                      & & 1334x_{1}^4 - 15360x_{1}^3 + 11520x_{1}^2 -5120x_{1} +2624\Big| \nonumber \\
                      & & \Big| x_{2}^4 + 12x_{2}^3 + 54x_{2}^2 +108x_{2} + 81\Big|\Big]^2 \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f(2, -3)$, $f(\textbf{x}^{*}) = 0$. \\

\item \textbf{Mishra 9 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
   f_{82}(\textbf{x}) &=& \Big[ab^2c + abc^2 + b^2 + (x_1 + x_2 - x_3)^2\Big]^2 \nonumber
\end{eqnarray}
where $ a = 2x_{1}^{3} + 5x_1x_2 + 4x_3 -2x_1^2x_3 -18 $, $b = x_{1} + x_2^3 + x_1x_3^2 - 22 $ \\
$ c = 8x_1^2 + 2x_2x_3 + 2x_2^2 + 3x_2^3 - 52$.
The global minimum is located at $\textbf{x}^{*} = f(1, 2, 3)$, $f(\textbf{x}^{*}) = 0$. \\


\item \textbf{Mishra 10 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
   f_{83}(\textbf{x}) &=& \Big[\lfloor x_{1} \perp x_{2}\rfloor - \lfloor x_{1} \rfloor - \lfloor x_{2} \rfloor\Big]^2 \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f\{(0, 0), (2, 2)\}$, $f(\textbf{x}^{*}) = 0$. \\


\item \textbf{Mishra 11 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
   f_{84}(\textbf{x}) &=& \Big[\frac{1}{D}\sum_{i=1}^{D}\big|x_i\big| - \big(\prod_{i=1}^{D}\big|x_i\big|\big)^{\frac{1}{N}}\Big]^2 \nonumber
\end{eqnarray}
The global minimum is $f(\textbf{x}^{*}) = 0$. \\

%% PARSOPOULOS FUNCTION
\item \textbf{Parsopoulos Function} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{85}(\textbf{x}) &=& \cos {\left( {{x_1}} \right)^2} + \sin {\left( {{x_2}} \right)^2} \nonumber
\end{eqnarray}
subject to $-5 \leq x_{i} \leq 5$, where $(x_{1},x_{2}) \in \mathbb{R}^{2}$.  This function has infinite number of global minima in $\mathbb{R}^{2}$, at points
$(\kappa\frac{\pi}{2}, \lambda \pi)$, where $\kappa = \pm 1,\pm 3,...$ and $\lambda = 0,\pm 1, \pm 2, ...$.  In the given domain problem, function has
12 global minima all equal to zero.

%% PEN-HOLDER FUNCTION (MISHRA 23.08.2006)
\item \textbf{Pen Holder Function} \cite{MISHRA2006_6}  (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
        \begin{eqnarray}
	       f_{86}(\textbf{x}) &=& -\exp[|\textrm{cos}(x_{1})\textrm{cos}(x_{2})
                                            e^{|1 - [(x_{1}^{2} + x_{2}^{2})]^{0.5}/\pi|}|^{-1}] \nonumber
        \end{eqnarray}
    subject to  $-11 \leq x_{i} \leq 11$.  The four global minima are located at $\textbf{x}^{*}$ = $f(\pm 9.646168$, $\pm 9.646168)$,
    $f(\textbf{x}^{*})= -0.96354 $. \\

\item \textbf{Pathological Function} \cite{RAHNAMAYAN2007} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{87}(\textbf{x}) &=& \sum_{i=1}^{D-1}\left(0.5 + \frac{\sin^2\sqrt{100x_{i}^2 + x_{i+1}^2} - 0.5}{1 + 0.001(x_{i}^2 -2x_{i}x_{i+1}+x_{i+1}^2)^2}\right) \nonumber
\end{eqnarray}
subject to $-100 \leq x_{i} \leq 100$.  The global minima is located $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0$. \\

%% PIVANI FUNCTION
 \item \textbf{Paviani Function} \cite{HIMMELBLAU1972} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
 \begin{eqnarray}
    f_{88}(\textbf{x}) & = &\sum\limits_{i = 1}^{10} {\left[ {{{\left( {\ln \left( {{x_i} - 2} \right)} \right)}^2} + {{\left( {\ln \left( {10 - {x_i}} \right)} \right)}^2}} \right]}  - {\left( {\prod\limits_{i = 1}^{10} {{x_i}} } \right)^{0.2}} \nonumber
\end{eqnarray}
subject to  $2.0001 \leq x_{i} \leq 10$, $i \in {1,2,...,10}$.  The global minimum is located at $\textbf{x}^{*} \approx f(9.351,....,9.351)$, $f(\textbf{x}^{*}) \approx -45.778 $. \\

%% PINTER FUNCTION
\item \textbf{Pint\'{e}r Function} \cite{PINTER1996} (Continuous, Differentiable, Non-separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{89}(\textbf{x}) &=& \sum\limits_{i = 1}^D {ix_i^2 + \sum\limits_{i = 1}^D {20i{{\sin }^2}A + } } \sum\limits_{i = 1}^D {i{{\log }_{10}}\left( {1 + i{B}^2} \right)} \nonumber
\end{eqnarray}
    where \\
    \begin{eqnarray}
        A &=& {\left( {{x_{i - 1}}\sin {x_i} + \sin {x_{i + 1}}} \right)} \nonumber \\
        B &=& {\left( {x_{i - 1}^2 - 2{x_i} + 3{x_{i + 1}} - \cos {x_i} + 1} \right)}\nonumber
    \end{eqnarray}
where $x_{0}= x_{D}$ and $x_{D+1} = x_{1}$, subject to  $-10 \leq x_{i} \leq 10$.
The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0 $. \\

% PERIODIC FUNCTION (http://www.gamsworld.org/performance/selconglobal/selcongloballib.htm)
\item \textbf{Periodic Function} \cite{ALI2005} (Separable)
\begin{eqnarray}
	       f_{90}(\textbf{x}) &=& 1 + \textrm{sin}^{2}(x_{1}) + \textrm{sin}^{2}(x_{2}) - 0.1e^{-(x_{1}^{2} + x_{2}^{2})} \nonumber
        \end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$, $f(\textbf{x}^{*}) = 0.9 $. \\
%%%%%%%%%%%%%%%%%%%%%%%%
% POWELL FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Powell Singular Function} \cite{POWELL1962} (Continuous, Differentiable, Non-Separable Scalable, Unimodal)
\begin{eqnarray}
    f_{91}(\textbf{x}) &=& \sum\limits_{i = 1}^{D/4} {{\left( {{x_{4i - 3}} + 10{x_{4i - 2}}} \right)}^2} \nonumber \\
                                & & + 5{{\left( {{x_{4i - 1}} - {x_{4i}}} \right)}^2} + {{\left( {{x_{4i - 2}} - {x_{4i - 1}}} \right)}^4} \nonumber \\
                                & & + 10{{\left( {{x_{4i - 3}} - {x_{4i}}} \right)}^4} \nonumber
\end{eqnarray}
subject to  $-4 \leq x_{i} \leq 5$.  The global minima is located at $\textbf{x}^{*} = f(3,-1,0,1,\cdots,3,-1,0,1)$, $f(\textbf{x}^{*}) = 0 $. \\


\item \textbf{Powell Singular 2 Function} \cite{FU2006} (Continuous, Differentiable, Non-Separable Scalable, Unimodal)
\begin{eqnarray}
    f_{92}(\textbf{x}) &=& \sum\limits_{i = 1}^{D-2} {{\left( {{x_{i - 1}} + 10{x_{i}}} \right)}^2} \nonumber \\
                                & & + 5{{\left( {{x_{i+1}} - {x_{i+2}}} \right)}^2} + {{\left( {{x_{i}} - {2x_{i + 1}}} \right)}^4} \nonumber \\
                                & & + 10{{\left( {{x_{i - 1}} - {x_{i+2}}} \right)}^4} \nonumber
\end{eqnarray}
subject to  $-4 \leq x_{i} \leq 5$.  The global minimum is $f(\textbf{x}^{*}) = 0 $.


\item \textbf{Powell Sum Function} \cite{RAHNAMAYAN2007} (Continuous, Differentiable, Separable Scalable, Unimodal)
\begin{eqnarray}
     f_{93}(\textbf{x}) &=& \sum_{i=1}^{D}\Big|x_{i}\Big|^{i+1} \nonumber
\end{eqnarray}
subject to  $-1 \leq x_{i} \leq 1$.  The global minimum is $f(\textbf{x}^{*}) = 0 $.

%% PRICE FUNCTION
\item \textbf{Price 1 Function} \cite{PRICE1977} (Continuous, Non-Differentiable, Separable Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{94}(\textbf{x}) &=& (|x_1| - 5)^2 + (|x_2| - 5)^2 \nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum are located at
$\textbf{x}^{*}$ =$ f(\{-5, -5\}$,$\{-5, 5\}$, $\{5, -5\}$, $\{5, 5\})$, $f(\textbf{x}^{*}) = 0$. \\


%% PRICE 2 FUNCTION
\item \textbf{Price 2 Function} \cite{PRICE1977} (Continuous, Differentiable, Non-Separable Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{95}(\textbf{x}) &=& 1 + \sin^2x_1 + \sin^2x_2 - 0.1e^{-x_1^2 - x_2^2} \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at
$\textbf{x}^{*} = f(0 \cdots 0)$, $f(\textbf{x}^{*}) = 0.9$. \\

%% PRICE 3 FUNCTION
\item \textbf{Price 3 Function} \cite{PRICE1977} (Continuous, Differentiable, Non-Separable Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{96}(\textbf{x}) &=& 100(x_2 - x_1^2)^2 + 6\Big[6.4(x_2 - 0.5)^2 - x_1 - 0.6 \Big]^2 \nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum are located at
$\textbf{x}^{*}$ =$ f(\{-5, -5\}$,$\{-5, 5\}$, $\{5, -5\}$, $\{5, 5\})$, $f(\textbf{x}^{*}) = 0$. \\


\item \textbf{Price 4 Function} \cite{PRICE1977} (Continuous, Differentiable, Non-Separable Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{97}(\textbf{x}) &=& (2 x_1^3 x_2 - x_2^3)^2 + (6 x_1 - x_2^2 + x_2) ^ 2 \nonumber
\end{eqnarray}
subject to $-500 \leq x_i \leq 500$.  The three global minima are located at $\textbf{x}^{*}$ =
$f(\{0, 0\}$,$\{2,4\}$, $\{1.464, -2.506\})$,
$f(\textbf{x}^{*}) = 0 $.

\item \textbf{Qing Function} \cite{QING2006} (Continuous, Differentiable, Separable Scalable, Multimodal)
\begin{eqnarray}
    f_{98}(\textbf{x}) &=& \sum_{i=1}^{D}(x_i^2 - i)^2 \nonumber
\end{eqnarray}
subject to $-500 \leq x_i \leq 500$.  The global minima are located at $\textbf{x}^{*} = f(\pm \sqrt{i})$,
$f(\textbf{x}^{*}) = 0 $.

%% QUADRATIC FUNCTION (MISHRA -- GLOBAL OPTIMIZATION BY PARTICLE SWARM--A FORTRAN PROGRAM)
\item \textbf{Quadratic Function} (Continuous, Differentiable, Non-Separable, Non-Scalable)
\begin{eqnarray}
	 f_{99}(\textbf{x}) &=& -3803.84 - 138.08x_{1} - 232.92x_{2} \nonumber \\
                                           & & + 128.08x_{1}^{2} \nonumber + 203.64x_{2}^{2} + 182.25x_{1}x_{2} \nonumber
        \end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f(0.19388, 0.48513)$, $f(\textbf{x}^{*}) = -3873.7243 $. \\


\item \textbf{Quartic Function} \cite{STORN1996} (Continuous, Differentiable, Separable, Scalable)
\begin{eqnarray}
	       f_{100}(\textbf{x}) &=&\sum_{i=1}^{D}ix_{i}^{4} + \textrm{random}[0,1) \nonumber
\end{eqnarray}
subject to  $-1.28 \leq x_{i} \leq 1.28$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0 $. \\

\item \textbf{Quintic Function} \cite{MISHRA2006_6}(Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{101}(\textbf{x}) &=& \sum_{i=1}^{D}\lvert x_{i}^5 - 3x_{i}^4 + 4x_{i}^3 + 2x_{i}^2 -10x_{i} - 4\rvert \nonumber
        \end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f($-1$ ~or~ $2$)$, $f(\textbf{x}^{*}) = 0 $. \\

%% RANA FUNCTION
\item \textbf{Rana Function} \cite{PRICE2005} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{102}(\textbf{x}) &=& \sum_{i=0}^{D-2}(x_{i+1} + 1)\textrm{cos}(t_{2})\textrm{sin}(t_{1}) + x_{i}*\textrm{cos}(t_{1})\textrm{sin}(t_{2}) \nonumber
\end{eqnarray}
subject to $-500 \leq x_{i} \leq 500$, where $t_{1} = \sqrt{\|x_{i+1} + x_{i} + 1\|}$ and $t_{2} = \sqrt{\|x_{i+1} - x_{i} + 1\|}$.

%% Ripple Functions
\item \textbf{Ripple 1 Function} (Non-separable)
\begin{eqnarray}
    f_{103}(\textbf{x}) &=& \sum_{i=1}^{2} -e^{\textrm{-2 ln2}(\frac{x_{i} - 0.1}{0.8})^2}(\textrm{sin}^{6}(5\pi x_{i}) + 0.1\textrm{cos}^2(500\pi x_{i})) \nonumber
\end{eqnarray}
subject to $0 \leq x_{i} \leq 1$.  It has one global minimum and 252004 local minima. The global form of the function
consists of $25$ holes, which forms a $5 \times 5$ regular grid.  Additionally, the whole function landscape is full of small
ripples caused by high frequency cosine function which creates a large number of local minima.

\item \textbf{Ripple 25 Function} (Non-separable)
\begin{eqnarray}
    f_{104}(\textbf{x}) &=& \sum_{i=1}^{2} -e^{\textrm{-2 ln2}(\frac{x_{i} - 0.1}{0.8})^2}(\textrm{sin}^{6}(5\pi x_{i})) \nonumber
\end{eqnarray}
subject to $0 \leq x_{i} \leq 1$.  It has one global form of the Ripple-1 function without any ripples due to absence of cosine
term.

%% ROSENBROCK FUNCTION
\item \textbf{Rosenbrock Function} \cite{ROSENBROCK1960} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{105}(\textbf{x}) &=& \sum_{i=1}^{D-1}\left[100(x_{i+1} - x_{i}^{2})^2 + (x_{i} - 1)^2\right] \nonumber
\end{eqnarray}
subject to  $-30 \leq x_{i} \leq 30$.  The global minima is located at $\textbf{x}^{*} = f(1,\cdots,1)$, $f(\textbf{x}^{*}) = 0$. \\

%% %% ROSENBROCK FUNCTION
\item \textbf{Rosenbrock Modified Function} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{106}(\textbf{x}) &=& 74 + 100(x_{2} - x_{1}^2)^2 + (1 - x)^2 \nonumber \\
                              & & - 400e^{-\frac{(x_{1} + 1)^2+(x_{2} + 1)^2}{0.1}} \nonumber
\end{eqnarray}
subject to  $-2 \leq x_{i} \leq 2$.  In this function, a Gaussian bump at $(-1,1)$ is added, which causes a local minimum at $(1,1)$ and global minimum
is located at $\textbf{x}^{*} = f(-1,-1)$, $f(\textbf{x}^{*}) = 0$.
This modification makes it a difficult to optimize because local minimum basin is larger than the global minimum basin. \\

\item \textbf{Rotated Ellipse Function} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
	       f_{107}(\textbf{x}) &=& 7x_1^2 - 6\sqrt{3}x_1x_2 + 13x_2^2  \nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f(0, 0)$, $f(\textbf{x}^{*}) = 0$. \\

\item \textbf{Rotated Ellipse 2 Function} \cite{PRICE2005} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
	       f_{108}(\textbf{x}) &=& x_1^2 - x_1x_2 + x_2^2  \nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f(0, 0)$, $f(\textbf{x}^{*}) = 0$. \\s

\item \textbf{Rump Function} \cite{MOORE1988} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
	       f_{109}(\textbf{x}) &=& (333.75 - x_1^2)x_2^6 + x_1^2(11x_1^2x_2^2 - 121x_2^4 - 2) + 5.5x_2^8 +\frac{x_1}{2x_2} \nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f(0, 0)$, $f(\textbf{x}^{*}) = 0$. \\

\item \textbf{Salomon Function} \cite{SALOMON1996} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{110}(\textbf{x}) &=& = 1 - \cos \Bigg(2\pi \sqrt{\sum_{i=1}^D x_i^2} \Bigg) + 0.1 \sqrt{\sum_{i=1}^D x_i^2} \nonumber
\end{eqnarray}
subject to $-100 \leq x_{i} \leq 100$. The global minimum is located at $\textbf{x}^{*} = f(0,0)$, $f(\textbf{x}^{*}) = 0$. \\

\item \textbf{Sargan Function} \cite{DIXON1978} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{111}(\textbf{x}) &=& = \sum_{i=1}{D}\Big(x_{i}^2 + 0.4\sum_{j\neq1}x_ix_j\Big) \nonumber
\end{eqnarray}
subject to $-100 \leq x_{i} \leq 100$. The global minimum is located at $\textbf{x}^{*} = f(0,\cdots, 0)$, $f(\textbf{x}^{*}) = 0$. \\

%% SCHAFFER 1 (MISHRA--23.08.2006)
\item  \textbf{Scahffer 1 Function} \cite{MISHRA2006_7} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    f_{112}(\textbf{x}) &=& 0.5  + \frac{\textrm{sin}^{2}(x_{1}^{2} + x_{2}^{2})^{2} - 0.5}{1 + 0.001(x_{1}^{2} + x_{2}^{2})^{2}} \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100 $.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$, $f(\textbf{x}^{*}) = 0$. \\

%% SCHAFFER 2 (MISHRA--23.08.2006)
\item  \textbf{Scahffer 2 Function} \cite{MISHRA2006_7} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    f_{113}(\textbf{x}) &=& 0.5  + \frac{\textrm{sin}^{2}(x_{1}^{2} - x_{2}^{2})^{2} - 0.5}{1 + 0.001(x_{1}^{2} + x_{2}^{2})^{2}} \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100 $.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$, $f(\textbf{x}^{*}) = 0$. \\

%% SCHAFFER 3 (MISHRA--23.08.2006)
\item  \textbf{Scahffer 3 Function} \cite{MISHRA2006_7} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    f_{114}(\textbf{x}) &=& 0.5  + \frac{\textrm{sin}^{2}\Big(\cos\Big|x_{1}^{2} - x_{2}^{2}\Big|\Big) - 0.5}{1 + 0.001(x_{1}^{2} + x_{2}^{2})^{2}} \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100 $.  The global minimum is located at $\textbf{x}^{*} = f(0,1.253115)$, $f(\textbf{x}^{*}) = 0.00156685$. \\

%% SCHAFFER 4 (MISHRA--23.08.2006)
\item  \textbf{Scahffer 4 Function} \cite{MISHRA2006_7} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    f_{115}(\textbf{x}) &=& 0.5  + \frac{\textrm{cos}^{2}\Big(\sin(x_{1}^{2} - x_{2}^{2})\Big) - 0.5}{1 + 0.001(x_{1}^{2} + x_{2}^{2})^{2}} \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100 $.  The global minimum is located at $\textbf{x}^{*} = f(0,1.253115)$, $f(\textbf{x}^{*}) = 0.292579$. \\

\item \textbf{Schmidt Vetters Function} \cite{LOOTSMA1972} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{116}(\textbf{x}) &=&  \frac{1}{1 + (x_1 - x_2)^2} + \sin\Big(\frac{\pi x_2 + x_3}{2} \Big) \nonumber \\
                        & & + e^{({\frac{x_1 + x_2}{x_2}}-2)^2} \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f(0.78547, 0.78547, 0.78547)$, $f(\textbf{x}^{*}) = 3$. \\


%% SCHUMER STEIGLITZ FUNCTION
\item \textbf{Schumer Steiglitz Function} \cite{SCHUMER1968} (Continuous, Differentiable, Separable, Scalable, Unimodal)
\begin{eqnarray}
    f_{117}(\textbf{x}) &=&  \sum_{i=1}^{^D}{x_{i}^4} \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f(0,\dots,0)$, $f(\textbf{x}^{*}) = 0$. \\

%% SCHWEFEL FUNCTION
\item \textbf{Schwefel Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Partially-Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{118}(\textbf{x}) &=&  \Big(\sum_{i=1}^{^D}{x_{i}^2}\Big)^{\alpha} \nonumber
\end{eqnarray}
where $\alpha \ge 0$, subject to  $-100 \leq x_{i} \leq 100$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$.\\

%% SCHWEFEL 1.2 FUNCTION
\item \textbf{Schwefel 1.2 Function} \cite{SCHWEFEL1981}  (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{119}(\textbf{x}) &=&  \sum_{i=1}^{^D}\left(\sum_{j=1}^{i}x_{j}\right)^2 \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$.\\

%% SCHWEFEL 2.4 FUNCTION
\item \textbf{Schwefel 2.4 Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{120}(\textbf{x}) &=&  \sum_{i=1}^{D}(x_{i} - 1)^2 + (x_1 - x_i^2)^2 \nonumber
\end{eqnarray}
subject to $0 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(1,\cdots,1)$,
$f(\textbf{x}^{*}) = 0$.\\

%% SCHWEFEL 2.6 FUNCTION
\item \textbf{Schwefel 2.6 Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    f_{121}(\textbf{x}) &=&  \max (|x_1 + 2x_2 -7|,|2x_1 + x_2 - 5|) \nonumber
\end{eqnarray}
subject to $-100 \leq x_{i} \leq 100$.  The global minima is located at $\textbf{x}^{*} = f(1,3)$,
$f(\textbf{x}^{*}) = 0$.\\

%% SCHWEFEL 2.20 FUNCTION
\item \textbf{Schwefel 2.20 Function} \cite{SCHWEFEL1981} (Continuous, Non-Differentiable, Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{122}(\textbf{x}) &=&  -\sum_{i=1}^{n}|x_{i}| \nonumber  % + \prod_{i = 1}^{n}|x_{i}| \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$.  \\

%% SCHWEFEL 2.21 FUNCTION
\item \textbf{Schwefel 2.21 Function} \cite{SCHWEFEL1981} (Continuous, Non-Differentiable, Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{123}(\textbf{x}) &=&  \underset{1\le i \le D}\max|x_{i}| \nonumber  % + \prod_{i = 1}^{n}|x_{i}| \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$.  \\

%% SCHWEFEL 2.22 FUNCTION
\item \textbf{Schwefel 2.22 Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{124}(\textbf{x}) &=&  \sum_{i=1}^{D}|x_{i}| + \prod_{i = 1}^{n}|x_{i}| \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$.  \\

%% SCHWEFEL 2.23 FUNCTION
\item \textbf{Schwefel 2.23 Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{125}(\textbf{x}) &=&  \sum_{i=1}^{D}x_{i}^{10} \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$.  \\

%% SCHWEFEL 2.23 FUNCTION
\item \textbf{Schwefel 2.23 Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
	       f_{126}(\textbf{x}) &=&  \sum_{i=1}^{D}x_{i}^{10} \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$.  \\

%% SCHWEFEL 2.25 FUNCTION
\item \textbf{Schwefel 2.25 Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
    f_{127}(\textbf{x}) &=&  \sum_{i=2}^{D}(x_{i} - 1)^2 + (x_1 - x_i^2)^2 \nonumber
\end{eqnarray}
subject to $0 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(1,\cdots,1)$,
$f(\textbf{x}^{*}) = 0$.\\

%% SCHWEFEL 2.26 FUNCTION
\item \textbf{Schwefel 2.26 Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{128}(\textbf{x}) &=& -\frac{1}{D}\sum_{i=1}^{D}x_{i}\sin{\sqrt{|x_{i}|}} \nonumber
\end{eqnarray}
subject to $-500 \leq x_{i} \leq 500$.  The global minimum is located at $\textbf{x}^{*} = \pm[\pi(0.5+k)]^2$,
$f(\textbf{x}^{*}) = -418.983$.\\

%% SCHWEFEL 2.36 FUNCTION
\item \textbf{Schwefel 2.36 Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{129}(\textbf{x}) &=& -x_1x_2(72 - 2x_1 -2x_2) \nonumber
\end{eqnarray}
subject to $0 \leq x_{i} \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f(12,\cdots,12)$,
$f(\textbf{x}^{*}) = -3456$.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%SHEKEL 5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Shekel 5} \cite{OPACIC1973} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{130}(\textbf{x}) &=& - \sum\limits_{i = 1}^5 {\frac{1}{{\sum\limits_{j = 1}^4 {{{\left( {{x_j} - {a_{ij}}} \right)}^2} + {c_i}} }}} \nonumber
\end{eqnarray}
where %\\ \\
$\textbf{A} = [A_{ij}] = \left[ {\begin{matrix}
4&4&4&4\\
1&1&1&1\\
8&8&8&8\\
6&6&6&6\\
3&7&3&7
\end{matrix}} \right]$, $\textbf{\underline{c}} = {c_i} = \left[ {\begin{matrix}
{0.1}\\
{0.2}\\
{0.2}\\
{0.4}\\
{0.4}
\end{matrix}} \right]$ \\

subject to $0 \leq x_{j} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(4, 4, 4, 4)$, $f(\textbf{x}^{*}) \approx -10.1499$.  \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%SHEKEL 7
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Shekel 7} \cite{OPACIC1973} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{131}(\textbf{x}) &=& - \sum\limits_{i = 1}^7 {\frac{1}{{\sum\limits_{j = 1}^4 {{{\left( {{x_j} - {a_{ij}}} \right)}^2} + {c_i}} }}} \nonumber
\end{eqnarray}
where %\\ \\
$\textbf{A} = [A_{ij}] = \left[ {\begin{matrix}
4&4&4&4\\
1&1&1&1\\
8&8&8&8\\
6&6&6&6\\
3&7&3&7\\
2&9&2&9\\
5&5&3&3
\end{matrix}} \right]$, $\textbf{\underline{c}} = {c_i} = \left[ {\begin{matrix}
{0.1}\\
{0.2}\\
{0.2}\\
{0.4}\\
{0.4}\\
{0.6}\\
{0.3}
\end{matrix}} \right]$ \\

subject to $0 \leq x_{j} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(4, 4, 4, 4)$, $f(\textbf{x}^{*}) \approx -10.3999$.  \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%SHEKEL 10
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Shekel 10} \cite{OPACIC1973} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
    f_{132}(\textbf{x}) &=& - \sum\limits_{i = 1}^{10} {\frac{1}{{\sum\limits_{j = 1}^4 {{{\left( {{x_j} - {a_{ij}}} \right)}^2} + {c_i}} }}} \nonumber
\end{eqnarray}
where % \\ \\
$\textbf{A} = [A_{ij}] = \left[ {\begin{matrix}
4&4&4&4\\
1&1&1&1\\
8&8&8&8\\
6&6&6&6\\
3&7&3&7\\
2&9&2&9\\
5&5&3&3 \\
8&1&8&1\\
6&2&6&2 \\
7&3.6&7&3.6
\end{matrix}} \right]$, $\textbf{\underline{c}} = {c_i} = \left[ {\begin{matrix}
{0.1}\\
{0.2}\\
{0.2}\\
{0.4}\\
{0.4}\\
{0.6}\\
{0.3}\\
{0.7}\\
{0.5}\\
{0.5}
\end{matrix}} \right]$ \\

subject to $0 \leq x_{j} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(4, 4, 4, 4)$, $f(\textbf{x}^{*}) \approx -10.5319$.  \\

%% SHUBERT FUNCTION (ALI05)
\item \textbf{Shubert Function} \cite{HENNART1982} (Continuous, Differentiable, Separable?, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{133}(\textbf{x}) &=&  \prod_{i=1}^{n}\left(\sum_{j=1}^{5}\textrm{cos}((j + 1)x_{i} + j)\right) \nonumber
\end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$, $i \in {1,2,\cdots,n}$.  The 18 global minima are located at
    $\textbf{x}^{*} = f(\{-7.0835, ~~4.8580\},    ~~\{-7.0835, -7.7083\},\\
          ~~~~~~~~~~~~~~~~~~~~~~~~\{-1.4251, -7.0835\},     ~~ \{~~5.4828,  ~~4.8580\},  \\
          ~~~~~~~~~~~~~~~~~~~~~~~~\{-1.4251, -0.8003\},     ~~ \{~~4.8580,  ~~5.4828\},  \\
          ~~~~~~~~~~~~~~~~~~~~~~~~\{-7.7083, -7.0835\},     ~~ \{-7.0835, -1.4251\}, \\
          ~~~~~~~~~~~~~~~~~~~~~~~~\{-7.7083, -0.8003\},     ~~ \{-7.7083,  ~~5.4828\}, \\
          ~~~~~~~~~~~~~~~~~~~~~~~~\{-0.8003, -7.7083\},     ~~ \{-0.8003, -1.4251\},  \\
          ~~~~~~~~~~~~~~~~~~~~~~~~\{-0.8003,~~4.8580\},     ~~ \{-1.4251,  ~~5.4828\}, \\
          ~~~~~~~~~~~~~~~~~~~~~~~~\{~~5.4828, -7.7083\},    ~~ \{~~4.8580, -7.0835\},  \\
          ~~~~~~~~~~~~~~~~~~~~~~~~\{~~5.4828, -1.4251\},    ~~ \{~~4.8580,  -0.8003\})$, \\
          $f(\textbf{x}^{*}) \simeq -186.7309 $.\\

%% SHUBERT FUNCTION (ALI05)
\item \textbf{Shubert 3 Function} \cite{ADORIO2005} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{134}(\textbf{x}) &=&  \left(\sum_{i=1}^{D}\sum_{j=1}^{5}j{\sin}((j + 1)x_{i} + j)\right) \nonumber
\end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is $f(\textbf{x}^{*}) \simeq -29.6733337 $ with multiple solutions.\\

%% SHUBERT FUNCTION (ALI05)
\item \textbf{Shubert 4 Function} \cite{ADORIO2005} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{135}(\textbf{x}) &=&  \left(\sum_{i=1}^{D}\sum_{j=1}^{5}j{\cos}((j + 1)x_{i} + j)\right) \nonumber
\end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is $f(\textbf{x}^{*}) \simeq -25.740858 $ with multiple solutions.\\

%% SCHAFFER 2 FUNCTION
\item \textbf{Schaffer F6 Function} \cite{SCHAFFER1989} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{136}(\textbf{x}) &=& \sum_{i=1}^{D} {0.5} + \frac{\sin^2{\sqrt{x_{i}^2 + x_{i+1}^2}} - 0.5}{\Big[1 + 0.001(x_{i}^2 + x_{i+1}^2)\Big]^2} \nonumber
        \end{eqnarray}
    subject to  $-100 \leq x_{i} \leq 100$.  The global minimum is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0 $.  \\

%%%%%%%%%%%%%%%%%%%%%%%%%%
%SPHERE FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Sphere Function} \cite{SCHUMER1968} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	f_{137}(\textbf{x}) &=& \sum_{i=1}^{D}x_{i}^{2} \nonumber
\end{eqnarray}
subject to  $0 \leq x_{i} \leq 10$. The global minima is located $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$. \nonumber \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STEP FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Step Function} (Discontinuous, Non-Differentiable, Separable, Scalable, Unimodal)
\begin{eqnarray}
	f_{138}(\textbf{x}) &=& \sum_{i=1}^{D}\left(\lfloor{|x_{i}|}\rfloor\right) \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$. The global minima is located $\textbf{x}^{*} = f(0,\cdots,0) = 0$,
$f(\textbf{x}^{*}) = 0$. \nonumber \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STEP 2 FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Step 2 Function} \cite{BAECK1993} (Discontinuous, Non-Differentiable, Separable, Scalable, Unimodal)
\begin{eqnarray}
	f_{139}(\textbf{x}) &=& \sum_{i=1}^{D}\left(\lfloor{x_{i} + 0.5}\rfloor\right)^2 \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$. The global minima is located $\textbf{x}^{*} = f(0.5,\cdots,0.5) = 0$,
$f(\textbf{x}^{*}) = 0$. \nonumber \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STEP 3 FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Step 3 Function} (Discontinuous, Non-Differentiable, Separable, Scalable, Unimodal)
\begin{eqnarray}
	f_{140}(\textbf{x}) &=& \sum_{i=1}^{D}\left(\lfloor{x_{i}^2}\rfloor\right) \nonumber
\end{eqnarray}
subject to  $-100 \leq x_{i} \leq 100$. The global minima is located $\textbf{x}^{*} = f(0,\cdots,0) = 0$,
$f(\textbf{x}^{*}) = 0$. \nonumber \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STEPINT FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Stepint Function} (Discontinuous, Non-Differentiable, Separable, Scalable, Unimodal)
\begin{eqnarray}
	f_{141}(\textbf{x}) &=& 25 + \sum_{i=1}^{D}\left(\lfloor{x_{i}}\rfloor\right) \nonumber
\end{eqnarray}
subject to  $-5.12 \leq x_{i} \leq 5.12$. The global minima is located $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$. \nonumber \\

\item \textbf{Streched V Sine Wave Function} \cite{SCHAFFER1989} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
	f_{142}(\textbf{x}) &=& \sum_{i=1}^{D-1}(x_{i+1}^{2} + x_{i}^{2})^{0.25}\Big[\sin^2\{50(x_{i+1}^{2} + x_{i}^{2})^{0.1}\} + 0.1\Big] \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$. The global minimum is located $\textbf{x}^{*} = f(0, 0)$,
$f(\textbf{x}^{*}) = 0$. \nonumber \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUM FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Sum Squares Function} \cite{HEDAR} (Continuous, Differentiable, Separable, Scalable, Unimodal)
\begin{eqnarray}
	f_{143}(\textbf{x}) &=& \sum_{i=1}^{D}ix_{i}^{2} \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$. The global minima is located $\textbf{x}^{*} = f(0,\cdots,0)$,
$f(\textbf{x}^{*}) = 0$. \nonumber \\

%% STYBLINSKI-TANG FUNCTION
\item \textbf{Styblinski-Tang Function} \cite{SILAGADZE2007} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{144}(\textbf{x}) &=&  \frac{1}{2}\sum_{i=1}^{n}(x_{i}^{4} - 16x_{i}^{2} + 5x_{i}) \nonumber
\end{eqnarray}
    subject to  $-5 \leq x_{i} \leq 5$. The global minimum is located $\textbf{x}^{*} = f(-2.903534,-2.903534)$, $f(\textbf{x}^{*}) = -78.332$.

%% HOLDER TABLE (MISHRA)
\item \textbf{Table 1 / Holder Table 1 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
    \begin{eqnarray}
        f_{145}(\textbf{x}) &=& -|\textrm{cos}(x_{1})\textrm{cos}(x_{2})e^{|1 - (x_{1} + x_{2})^{0.5}/\pi|}|    \nonumber
    \end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.

    The four global minima are located at $\textbf{x}^{*}$ = $f(\pm 9.646168$, $\pm 9.646168)$,
    $f(\textbf{x}^{*}) = -26.920336 $.  \\

% HOLDER TABLE Modified (Momin)
\item \textbf{Table 2 / Holder Table 2 Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
    \begin{eqnarray}
        f_{146}(\textbf{x}) &=& -|\textrm{sin}(x_{1})\textrm{cos}(x_{2})e^{|1 - (x_{1} + x_{2})^{0.5}/\pi|}|    \nonumber
    \end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.

    The four global minima are located at
    $\textbf{x}^{*}$ = $f(\pm 8.055023472141116$, $\pm 9.664590028909654)$,
    $f(\textbf{x}^{*})$ = $-19.20850 $.  \\

%% CARROM TABLE
\item \textbf{Table 3 / Carrom Table Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
        \begin{eqnarray}
	       f_{147}(\textbf{x}) &=& -[(\textrm{cos}(x_{1})\textrm{cos}(x_{2}) \nonumber \\
                                           & & \exp|1 - [(x_{1}^{2} + x_{2}^{2})^{0.5}]/\pi|)^{2}]/30 \nonumber
        \end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.

    The four global minima are located at $\textbf{x}^{*}$ = $f(\pm 9.646157266348881$, $\pm 9.646134286497169)$,
    $f(\textbf{x}^{*}) = -24.1568155$.  \\

%% TEST-TUBE HOLDER FUNCTION
\item \textbf{Testtube Holder Function} \cite{MISHRA2006_6} (Continuous, Differentiable, Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{148}(\textbf{x}) &=& -4\big[(\textrm{sin}(x_{1})\textrm{cos}(x_{2}) \nonumber \\
                                           & & e^{|\textrm{cos}[(x_{1}^{2} + x_{2}^{2})/{200}]|})\big] \nonumber
\end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The two global minima are located at $\textbf{x}^{*} = f(\pm \pi/2, 0)$, $f(\textbf{x}^{*}) = -10.872300$.  \\

%%TRECANNI FUNCTION
\item \textbf{Trecanni Function} \cite{DIXON1978} (Continuous, Differentiable, Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
	       f_{149}(\textbf{x}) &=&  x_{1}^{4} - 4x_{1}^{3} + 4x_{1} + x_{2}^2 \nonumber
\end{eqnarray}
    subject to  $-5 \leq x_{i} \leq 5$.  The two global minima are located at $\textbf{x}^{*} = f(\{0,0\}, \{-2, 0\})$, $f(\textbf{x}^{*}) = 0$.

\item \textbf{Trid 6 Function} \cite{HEDAR} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{150}(\textbf{x}) &=&  \sum_{i=1}^{D}\left(x_{i} - 1 \right)^{2} - \sum_{i=1}^{D}x_{i}x_{i-1} \nonumber
\end{eqnarray}
    subject to  $-6^2 \leq x_{i} \leq 6^2$.  The global minima is located at $f(\textbf{x}^{*}) = -50$. \nonumber \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TRID 10 FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Trid 10 Function} \cite{HEDAR} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{151}(\textbf{x}) &=&  \sum_{i=1}^{D}\left(x_{i} - 1 \right)^{2} - \sum_{i=1}^{D}x_{i}x_{i-1} \nonumber
\end{eqnarray}
    subject to  $-100 \leq x_{i} \leq 100$.  The global minima is located at $f(\textbf{x}^{*}) = -200$. \nonumber \\

%%TREFETHEN FUNCTION
\item \textbf{Trefethen Function} \cite{ADORIO2005} (Continuous, Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{152}(\textbf{x}) &=&  e^{\textrm{sin}(50x_{1})} + \textrm{sin}(60e^{x_{2}}) \nonumber \\
                                           & & + \textrm{sin}(70\textrm{sin}(x_{1})) + \textrm{sin}(\textrm{sin}(80x_{2})) \nonumber \\
    		                               & &  - \textrm{sin}(10(x_{1} + x_{2})) + \frac{1}{4}(x_{1}^{2} + x_{2}^{2}) \nonumber
\end{eqnarray}
    subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*} = f(-0.024403,0.210612)$, $f(\textbf{x}^{*}) = -3.30686865$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TRIGONOMETRIC FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Trigonometric 1 Function} \cite{DIXON1978} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)

\begin{eqnarray}
	       f_{153}(\textbf{x}) &=&  \sum_{i=1}^{D}[D - \sum_{j=1}^{D}\cos{x_{j}} \nonumber \\
                                           & & + i(1 - \cos(x_{i}) - \sin(x_{i}))]^{2} \nonumber
\end{eqnarray}
subject to  $0 \leq x_{i} \leq pi$.  The global minimum is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0$ \nonumber \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TRIGONOMETRIC FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item \textbf{Trigonometric 2 Function} \cite{FU2006} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{154}(\textbf{x}) &=&  1 + \sum_{i=1}^{D} 8\sin^2\big[7(x_i - 0.9)^2\big] + 6\sin^2\big[14(x_1 - 0.9)^2\big] + (x_i - 0.9)^2\nonumber
\end{eqnarray}
subject to  $-500 \leq x_{i} \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f(0.9,\cdots,0.9)$, $f(\textbf{x}^{*}) = 1$ \nonumber \\


%%TRIPOD FUNCTION
\item \textbf{Tripod Function} \cite{RAHNAMAYAN2007} (Discontinuous, Non-Differentiable, Non-Separable, Non-Scalable, Multimodal)
\begin{eqnarray}
	       f_{155}(\textbf{x}) &=& p(x_{2})(1 + p(x_{1})) \nonumber \\
                                           & & + |x_{1} + 50p(x_{2})(1-2p(x_{1}))| \nonumber \\
                                           & & + |x_{2} + 50(1 - 2p(x_{2}))| \nonumber
\end{eqnarray}
    subject to  $-100 \leq x_{i} \leq 100$, where $ p(x) = 1 $ for $x \geq 0$.  The global minimum is located at $\textbf{x}^{*} = f(0,-50)$, $f(\textbf{x}^{*}) = 0$. \\

%% URSEM FUNCTIONS
%% URSEM-1 Function
\item \textbf{Ursem 1 Function} \cite{ROENKKOENEN2009} (Separable)
\begin{eqnarray}
	       f_{156}(\textbf{x}) &=& -\textrm{sin}(2x_{1} - 0.5\pi) - 3\textrm{cos}(x_{2}) - 0.5x_{1} \nonumber
\end{eqnarray}
    subject to  $-2.5 \leq x_{1} \leq 3$ and $-2 \leq x_{2} \leq 2$, and has single global and local minima.

%% URSEM-3 Function
\item \textbf{Ursem 3 Function} \cite{ROENKKOENEN2009}(Non-separable)
\begin{eqnarray}
	       f_{157}(\textbf{x}) &=& -\textrm{sin}(2.2\pi x_{1} + 0.5\pi).\frac{2 - \left|x_{1}\right|}{2}.\frac{3 - \left|x_{1}\right|}{2} \nonumber \\
& & -\textrm{sin}(0.5\pi x_{2}^2 + 0.5\pi).\frac{2 - \left|x_{2}\right|}{2}.\frac{3 - \left|x_{2}\right|}{2}\nonumber
\end{eqnarray}
    subject to  $-2 \leq x_{1} \leq 2$ and $-1.5 \leq x_{2} \leq 1.5$, and has single global minimum and four regularly spaced local minima
    positioned in a direct line, such that global minimum is in the middle.

%% URSEM-4 Function
\item \textbf{Ursem 4 Function} \cite{ROENKKOENEN2009} (Non-separable)

\begin{eqnarray}
	       f_{158}(\textbf{x}) &=& -3\textrm{sin}(0.5\pi x_{1} + 0.5\pi).\frac{2 - \sqrt{x_{1}^2 + x_{2}^2}}{4} \nonumber
\end{eqnarray}
    subject to  $-2 \leq x_{i} \leq 2$, and has single global minimum positioned at the middle and four local minima
    at the corners of the search space.

%% URSEM-WAVE Function
\item \textbf{Ursem Waves Function} \cite{ROENKKOENEN2009}(Non-separable)
\begin{eqnarray}
	       f_{159}(\textbf{x}) &=& -0.9x_{1}^2 + (x_{2}^2 - 4.5x_{2}^2)x_{1}x_{2} \nonumber \\
                                           & & +4.7\textrm{cos}(3x_{1} - x_{2}^2(2 + x_{1}))\textrm{sin}(2.5\pi x_{1}) \nonumber
\end{eqnarray}
    subject to  $-0.9 \leq x_{1} \leq 1.2$ and $-1.2 \leq x_{2} \leq 1.2$, and has single global minimum and nine irregularly spaced
    local minima in the search space.

%% VS FUNCTION(VENTER Sobiezcczanski-Sobieski Function) (SPSO)
\item \textbf{Venter Sobiezcczanski-Sobieski Function} \cite{BEGAMBRE2009} (Continuous, Differentiable, Separable, Non-Scalable)
\begin{eqnarray}
	       f_{160}(\textbf{x}) &=& x_{1}^{2} - 100\textrm{cos}(x_1)^{2} \nonumber \\
                                           & & - 100\textrm{cos}(x_{1}^{2}/30) + x_{2}^{2} \nonumber \\
                                           & & - 100\textrm{cos}(x_{2})^{2} - 100\textrm{cos}(x_{2}^{2}/30) \nonumber
\end{eqnarray}
    subject to  $-50 \leq x_{i} \leq 50$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$, $f(\textbf{x}^{*}) = -400$. \\

%% WATSON FUNCTION
\item \textbf{Watson Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
  f_{161}(\textbf{x}) &=& \sum_{i = 0} ^{29}   \{ \sum_{j = 0}^4 ((j-1) a_i^j x_{j+1}) - \left[ \sum_{j = 0}^5 a_i^j x_{j+1} \right]^2 - 1\}^2 + x_1^2 \nonumber
\end{eqnarray}
subject to $|x_i| \le 10$, where the coefficient $a_i = i / 29.0$. The global minimum is located at $\textbf{x}^{*} = f(-0.0158, 1.012, -0.2329, 1.260, -1.513, 0.9928)$,
$f(\textbf{x}^{*}) = 0.002288$.\\

%% WAYBURN Seader 1 Function
\item \textbf{Wayburn Seader 1 Function} \cite{WAYBURN1987} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
  f_{162}(\textbf{x}) &=& (x_1^6 + x_2^4 - 17)^2 + (2x_1 + x_2 - 4)^2 \nonumber
\end{eqnarray}
The global minimum is located at $\textbf{x}^{*} = f\{(1,2), (1.597, 0.806)\}$,
$f(\textbf{x}^{*}) = 0$.\\

%% WAYBURN Seader 2 Function
\item \textbf{Wayburn Seader 2 Function} \cite{WAYBURN1987} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
  f_{163}(\textbf{x}) &=& \Big[1.613 - 4(x_1 - 0.3125)^2 - 4(x_2 - 1.625)^2\Big]^2 + (x_2 - 1)^2 \nonumber
\end{eqnarray}
subject to $-500 \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f\{(0.2, 1), (0.425, 1)\}$,
$f(\textbf{x}^{*}) = 0$.\\

%% WAYBURN Seader 3 Function
\item \textbf{Wayburn Seader 3 Function} \cite{WAYBURN1987} (Continuous, Differentiable, Non-Separable, Scalable, Unimodal)
\begin{eqnarray}
  f_{164}(\textbf{x}) &=& 2\frac{x_1^3}{3} - 8x_1^2 + 33x_1 - x_1x_2 + 5 + \Big[(x_1 - 4)^2 + (x_2 - 5)^2 - 4\Big]^2 \nonumber
\end{eqnarray}
subject to $-500 \leq 500$.  The global minimum is located at $\textbf{x}^{*} = f(5.611, 6.187)$,
$f(\textbf{x}^{*}) = 21.35$.\\


%% W-FUNCTION
\item \textbf{W / Wavy Function} \cite{COURRIEU1997} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	f_{165}(\textbf{x}) &=& 1 - \frac{1}{D}\sum\limits_{i = 1}^D \textrm{cos}(kx_{i})e^\frac{-x_{i}^2}{2}\nonumber
\end{eqnarray}
subject to  $-\pi \leq x_{i} \leq \pi$.  The global minimum is located at $\textbf{x}^{*} = f(0,0)$, $ f(\textbf{x}^{*})= 0$.\\
The number of local minima is $kn$ and $(k+1)n$ for odd and even $k$ respectively.  For $D=2$ and $k=10$, there are 121 local minima.

%%WEIERSTRASS FUNCTION
\item \textbf{Weierstrass Function} \cite{SUGANTHAN2005}(Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{166}(\textbf{x}) &=& \sum_{i=1}^{n}[\sum_{k=0}^{kmax}a^{k}\textrm{cos}(2 \pi b^{k}(x_{i} + 0.5)) \nonumber \\
                                           & & - n\sum_{k=0}^{kmax}a^{k}\textrm{cos}(\pi b^{k})] \nonumber
\end{eqnarray}
    subject to  $-0.5 \leq x_{i} \leq 0.5$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0$. \\

%% WHITLEY FUNCTION

\item \textbf{Whitley Function} \cite{WHITLEY1996} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)

\begin{eqnarray}
    f_{167}(\textbf{x}) &=& \sum_{i=1}^D\sum_{j=1}^D\big[\frac{(100(x_{i}^2 - x_{j})^2 + (1 - x_{j})^2)^2}{4000} \nonumber \\
    & & - \textrm{cos}\left(100(x_{i}^2 - x_{j})^2 + (1 - x_{j})^2 + 1\right)\big]\nonumber
\end{eqnarray}
combines a very steep overall slope with a highly multimodal area around the global minimum located at $x_{i}=1$, where $i = 1,...,D$.

%% WOLFE FUNCTION
\item \textbf{Wolfe Function} \cite{SCHWEFEL1981} (Continuous, Differentiable, Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{168}(\textbf{x}) &=& \frac{4}{3}(x_1^2 + x_2^2 - x_{1}x_{2})^0.75 + x_3
\end{eqnarray}
    subject to  $0 \leq x_{i} \leq 2$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0$. \\

\item \textbf{Xin-She Yang (Function 1)} (Separable)\\
This is a generic stochastic and non-smooth function proposed in \cite{YANG2010a,Yang2010b}.
\begin{eqnarray}
            f_{169}(\textbf{x}) &=& \sum_{i=1}^{D}\epsilon_{i}\abs{x_{i}}^{i} \nonumber
\end{eqnarray}

subject to  $-5 \leq x_{i} \leq 5$.  The variable $\epsilon_{i}, (i=1,2,\cdots,D)$ is a random variable uniformly distributed in $[0,1]$.
The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0$.  \\

\item \textbf{Xin-She Yang (Function 2)}(Non-separable)
\begin{eqnarray}
	       %f_{}(\textbf{x}) &=& \sum_{i=1}^{D}e^{-\sum_{i=1}^{D}\sin(x_{1}^2)} \nonumber
            f_{170}(\textbf{x}) &=& \big(\sum_{i=1}^{D}\abs{x_{i}}\big)\exp\big[-\sum_{i=1}^{D}\textrm{sin}(x_{i}^2)\big] \nonumber
\end{eqnarray}

subject to  $-2\pi \leq x_{i} \leq 2\pi$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = 0$.  \\

\item \textbf{Xin-She Yang (Function 3)} (Non-separable)
\begin{eqnarray}
	       f_{171}(\textbf{x}) &=& \left[e^{-\sum_{i=1}^{D}(x_{i}/\beta)^{2m}} - 2e^{-\sum_{i=1}^{D}(x_{i})^{2}}.\prod_{i=1}^{D}\cos^2(x_{i})\right]\nonumber
\end{eqnarray}
subject to  $-20 \leq x_{i} \leq 20$.  The global minima for $m=5$ and $\beta=15$ is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = -1$. \\


\item \textbf{Xin-She Yang (Function 4)} (Non-separable)
\begin{eqnarray}
	       f_{172}(\textbf{x}) &=& \left[{\sum_{i=1}^{D} \sin^{2}(x_{i})} - e^{-\sum_{i=1}^{D}x_{i}^2}\right].e^{-\sum_{i=1}^{D}\sin^2\sqrt{{|x_{i}|}}} \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$, $f(\textbf{x}^{*}) = -1$. \\



%ZAKHAROV  FUNCTION
\item \textbf{Zakharov Function} \cite{RAHNAMAYAN2007} (Continuous, Differentiable, Non-Separable, Scalable, Multimodal)
\begin{eqnarray}
	       f_{173}(\textbf{x}) &=& \sum_{i=1}^{n} x_{i}^{2} + \left(\frac{1}{2}\sum_{i=1}^{n}ix_{i}\right)^2
                                            + \left(\frac{1}{2}\sum_{i=1}^{n}ix_{i}\right)^4 \nonumber
\end{eqnarray}
    subject to  $-5 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(0,\cdots,0)$,
    $f(\textbf{x}^{*}) = 0$. \nonumber \\

%ZETTL FUNCTION
\item \textbf{Zettl Function} \cite{SCHWEFEL1995} (Continuous, Differentiable, Non-Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
	       f_{174}(\textbf{x}) &=& (x_{1}^{2} + x_{2}^{2} - 2x_{1})^{2} + 0.25 x_{1} \nonumber
\end{eqnarray}
    subject to  $-5 \leq x_{i} \leq 10$.  The global minima is located at $\textbf{x}^{*} = f(-0.0299, 0)$, $f(\textbf{x}^{*}) = -0.003791$. \\

%% ALIFFI-PENTINI
\item \textbf{Zirilli or Aluffi-Pentini's Function} \cite{ALI2005} (Continuous, Differentiable, Separable, Non-Scalable, Unimodal)
\begin{eqnarray}
    %f_{}(\textbf{x}) &=&  0.25x_{1}^{4} - 0.5x_{1}^{2} + 0.1x_{1} + 0.5x_{2}^{2} \nonumber
    f_{175}(\textbf{x}) &=&  0.25x_{1}^{4} - 0.5x_{1}^{2} + 0.1x_{1} + 0.5x_{2}^{2} \nonumber
\end{eqnarray}
subject to  $-10 \leq x_{i} \leq 10$.  The global minimum is located at $\textbf{x}^{*}=(-1.0465,0)$, $f(\textbf{x}^{*}) \approx -0.3523 $. \\

\end{enumerate}

\section{Conclusions}

Test functions are important to validate and compare optimization algorithms, especially newly developed algorithms.
Here, we have attempted to provide the most comprehensive list of known benchmarks or test functions. However,
it is may be possibly that we have missed some functions, but this is not intentional. This list is based on
all the literature known to us by the time of writing.
It can be expected that all these functions should be used for testing new optimization algorithms so as to
provide a more complete view about the performance of any algorithms of interest.


